### 2024-01-02 code/codeprocessfemale.Rmd
code used to generate female gymnast figures and data

---
title: "female code"
output: html_document
---

```{r packages}
# Load packages
library(tidyverse)
library(dplyr)
library(ggplot2)
library(readr)
```
```{r Functions}
# Read the CSV file
data <- read.csv("../gym2024data/cleandata/data_2022_2023.csv", header = TRUE)

#Convert all last names to lower case
data$LastName <- tolower(data$LastName)

#Remove rows with scores equal to zero
data <- data %>% filter(Score != 0)

#Combine VT, VT1, and VT2 in the "Apparatus" column
data$Apparatus <- ifelse(data$Apparatus %in% c("VT", "VT1", "VT2"), "VT", data$Apparatus)

#Calculate the mean and standard deviation of each United States female gymnast's score for each apparatus
usa_female_scores <- data %>%
  filter(Country == "USA" & Gender == "w") %>%
  group_by(Apparatus, LastName) %>%
  summarize(
    Mean_Score = mean(Score),
    SD_Score = sd(Score)
  )

#Add a "Number of Observations" column to the usa_female_scores table
usa_female_scores <- data %>%
  filter(Country == "USA" & Gender == "w") %>%
  group_by(Apparatus, LastName) %>%
  summarize(
    Num_Observations = n(),
    Mean_Score = mean(Score),
    SD_Score = sd(Score)
  )

#Create a table with the top 10 athletes with the highest mean scores for each apparatus and to plot each apparatus on separate graphs
  # Filter for USA female gymnasts
  usa_female_scores <- data %>%
  filter(Country == "USA" & Gender == "w")

  # Group by apparatus, calculate mean, standard deviation, and number of observations
  usa_female_scores <- usa_female_scores %>%
  group_by(Apparatus, LastName) %>%
  summarize(
    Num_Observations = n(),
    Mean_Score = mean(Score),
    SD_Score = sd(Score)
   )

  # Create a table with the top 10 athletes for each apparatus
  top_10_athletes <- usa_female_scores %>%
  group_by(Apparatus) %>%
  arrange(Apparatus, desc(Mean_Score)) %>%
  slice_head(n = 10)

  # Plot each apparatus on separate graphs
  for (apparatus in unique(top_10_athletes$Apparatus)) {
  data_subset <- filter(top_10_athletes, Apparatus == apparatus)
  p <- ggplot(data_subset, aes(x = SD_Score, y = Mean_Score, label = LastName)) +
    geom_point() +
    geom_text(hjust = 0, vjust = 0) +
    labs(title = paste("Top 10 Athletes in", apparatus),
         x = "Standard Deviation", y = "Mean Score")
  print(p)
  }

  # Print the table of top 10 athletes
  top_10_athletes

#Add a "Mean minus Standard Deviation" column to the top_10_athletes table
  # Calculate the mean minus standard deviation
  top_10_athletes <- top_10_athletes %>%
  mutate(Mean_minus_SD = Mean_Score - SD_Score)

  # Print the table of top 10 athletes
  top_10_athletes

#Add a "Mean minus (0.5) x Standard Deviation" column to the top_10_athletes table
  # Calculate the mean minus (0.5) x standard deviation
top_10_athletes <- top_10_athletes %>%
  mutate(Mean_minus_0.5xSD = Mean_Score - 0.5 * SD_Score)

  # Print the table of top 10 athletes
  top_10_athletes

#Calculate the means and standard deviations for the specified US female athletes across all apparatuses
 # Filter for USA female athletes
  usa_female_scores <- data %>%
  filter(Country == "USA" & Gender == "w")

  # Define the list of last names
  target_last_names <- c("biles", "mcclain", "blakely", "sumanasekera", "jones", "carey", "chiles", "matthews", "wong", "lincoln", "dicello")

  # Filter the data for the specified athletes
  selected_athletes <- usa_female_scores %>%
  filter(LastName %in% target_last_names)

  # Group by athlete, apparatus, and calculate mean and standard deviation
  athlete_apparatus_scores <- selected_athletes %>%
  group_by(LastName, Apparatus) %>%
  summarize(
    Mean_Score = mean(Score),
    SD_Score = sd(Score)
  )

  # Print the results
  print(athlete_apparatus_scores)

#Calculate the sum of means and standard deviations for the targeted athletes from the athlete_apparatus_scores table
  # Define the list of last names
  target_last_names <- c("biles", "mcclain", "blakely", "sumanasekera", "jones", "carey", "chiles", "matthews", "wong", "lincoln", "dicello")

  # Filter the data for the specified athletes
  selected_athletes_scores <- athlete_apparatus_scores %>%
  filter(LastName %in% target_last_names)

  # Group by athlete and calculate the sums of means and standard deviations
  sums <- selected_athletes_scores %>%
  group_by(LastName) %>%
  summarize(
    Sum_Means = sum(Mean_Score),
    Sum_SD = sum(SD_Score)
  )

  # Print the sums for each athlete
  print(sums)

#Create a scatter plot of the summed means on the y-axis and summed standard deviations on the x-axis
  # Create a scatter plot
  p <- ggplot(sums, aes(x = Sum_SD, y = Sum_Means, label = LastName)) +
  geom_point() +
  geom_text(hjust = 0, vjust = 0) +
  labs(x = "Sum of Standard Deviations", y = "Sum of Means", title = "Female All-Around Candidates")

  # Display the plot
  print(p)

#Calculate and display the mean score and standard deviation sum for every combination of 3 athletes from the sums table
  # Calculate all combinations of 3 athletes
  athlete_combinations <- combn(sums$LastName, 3)

  # Create a data frame to store the results
  combinations_results <- data.frame(
  Combination = character(choose(length(sums$LastName), 3)),
  Mean_Score = numeric(choose(length(sums$LastName), 3)),
  SD_Sum = numeric(choose(length(sums$LastName), 3))
  )

  # Calculate and store the mean and standard deviation sum for each combination
  for (i in 1:ncol(athlete_combinations)) {
  combination <- athlete_combinations[, i]
  mean_scores <- sums$Sum_Means[sums$LastName %in% combination]
  sd_sums <- sums$Sum_SD[sums$LastName %in% combination]
  combinations_results$Combination[i] <- paste(combination, collapse = ", ")
  combinations_results$Mean_Score[i] <- sum(mean_scores)
  combinations_results$SD_Sum[i] <- sum(sd_sums)
  }

  # Print the results
  print(combinations_results)

#Plot the mean (y-axis) vs. standard deviation (x-axis) for the 10 combinations with the highest mean score from the combinations_results table
  # Sort the combinations by mean score in descending order and select the top 10
  top_10_combinations <- head(combinations_results[order(-combinations_results$Mean_Score), ], 10)

  # Create a scatter plot for the top 10 combinations
  p <- ggplot(top_10_combinations, aes(x = SD_Sum, y = Mean_Score)) +
  geom_point() +
  geom_text(aes(label = Combination), hjust = 0, vjust = 0) +
  labs(x = "Sum of Standard Deviations", y = "Mean Score") +
  ggtitle("Top 10 Combinations with Highest Mean Score")

  # Display the plot
  print(p)

#Calculate and display the mean score and standard deviation sum for every combination of 4 athletes from the sums table
  # Calculate all combinations of 4 athletes
  athlete_combinations_4 <- combn(sums$LastName, 4)

  # Create a data frame to store the results
  combinations_results_4 <- data.frame(
  Combination = character(choose(length(sums$LastName), 4)),
  Mean_Score = numeric(choose(length(sums$LastName), 4)),
  SD_Sum = numeric(choose(length(sums$LastName), 4))
  )

  # Calculate and store the mean and standard deviation sum for each combination
  for (i in 1:ncol(athlete_combinations_4)) {
  combination <- athlete_combinations_4[, i]
  mean_scores <- sums$Sum_Means[sums$LastName %in% combination]
  sd_sums <- sums$Sum_SD[sums$LastName %in% combination]
  combinations_results_4$Combination[i] <- paste(combination, collapse = ", ")
  combinations_results_4$Mean_Score[i] <- sum(mean_scores)
  combinations_results_4$SD_Sum[i] <- sum(sd_sums)
  }

  # Print the results
  print(combinations_results_4)

#Plot the mean (y-axis) vs. standard deviation (x-axis) for the 10 combinations with the highest mean score from the combinations_results_4 table
  # Sort the combinations by mean score in descending order and select the top 10
  top_10_combinations_4 <- head(combinations_results_4[order(-combinations_results_4$Mean_Score), ], 10)

  # Create a scatter plot for the top 10 combinations
  p <- ggplot(top_10_combinations_4, aes(x = SD_Sum, y = Mean_Score)) +
  geom_point() +
  geom_text(aes(label = Combination), hjust = 0, vjust = 0) +
  labs(x = "Sum of Standard Deviations", y = "Mean Score") +
  ggtitle("Top 10 Combinations with Highest Mean Score (4 Athletes)")

  # Display the plot
  print(p)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

### 2024-01-03 code/codeprocessfemale.Rmd
reattempting to edit code to specify female in figure labels

@@
 # Read the CSV file
-data <- read.csv("../gym2024data/cleandata/data_2022_2023.csv", header = TRUE)
+data <- read.csv("../KH-UCSAS-Submission/gym2024data/cleandata/data_2022_2023.csv", header = TRUE)
 
@@
     geom_text(hjust = 0, vjust = 0) +
-    labs(title = paste("Top 10 Athletes in", apparatus),
+    labs(title = paste("Top 10 Female Athletes in", apparatus),
          x = "Standard Deviation", y = "Mean Score")
@@
   labs(x = "Sum of Standard Deviations", y = "Mean Score") +
-  ggtitle("Top 10 Combinations with Highest Mean Score")
+  ggtitle("Top 10 Combinations of 3 Female Athletes with Highest Mean Score")
 
@@
   labs(x = "Sum of Standard Deviations", y = "Mean Score") +
-  ggtitle("Top 10 Combinations with Highest Mean Score (4 Athletes)")
+  ggtitle("Top 10 Combinations of 4 Female Athletes with Highest Mean Score")
 
@@
 ```
-
-## R Markdown
-
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:

### 2024-01-03 code/codeprocessmale.Rmd
adding code used for processing male data

--- 2024-01-03 code/codeprocessfemale.Rmd
@@
 ---
-title: "female code"
+title: "male code"
 output: html_document
@@
 
-#Calculate the mean and standard deviation of each United States female gymnast's score for each apparatus
-usa_female_scores <- data %>%
-  filter(Country == "USA" & Gender == "w") %>%
+#Calculate the mean and standard deviation of each male gymnast's score for each apparatus
+male_scores <- data %>%
+  filter(Gender == "m") %>%
+  group_by(Apparatus, LastName, FirstName) %>%
+  summarize(
+    Mean_Score = mean(Score),
+    SD_Score = sd(Score)
+  )
+
+#Calculate the mean and standard deviation of each United States male gymnast's score for each apparatus
+usa_male_scores <- data %>%
+  filter(Country == "USA" & Gender == "m") %>%
   group_by(Apparatus, LastName) %>%
@@
 
-#Add a "Number of Observations" column to the usa_female_scores table
-usa_female_scores <- data %>%
-  filter(Country == "USA" & Gender == "w") %>%
+#Add a "Number of Observations" column to the usa_male_scores table
+usa_male_scores <- data %>%
+  filter(Country == "USA" & Gender == "m") %>%
   group_by(Apparatus, LastName) %>%
@@
 #Create a table with the top 10 athletes with the highest mean scores for each apparatus and to plot each apparatus on separate graphs
-  # Filter for USA female gymnasts
+  # Filter for USA male gymnasts
   usa_female_scores <- data %>%
-  filter(Country == "USA" & Gender == "w")
+  filter(Country == "USA" & Gender == "m")
 
   # Group by apparatus, calculate mean, standard deviation, and number of observations
-  usa_female_scores <- usa_female_scores %>%
+  usa_male_scores <- usa_male_scores %>%
   group_by(Apparatus, LastName) %>%
@@
   # Create a table with the top 10 athletes for each apparatus
-  top_10_athletes <- usa_female_scores %>%
+  top_10_athletes <- usa_male_scores %>%
   group_by(Apparatus) %>%
@@
     geom_text(hjust = 0, vjust = 0) +
-    labs(title = paste("Top 10 Female Athletes in", apparatus),
+    labs(title = paste("Top 10 Male Athletes in", apparatus),
          x = "Standard Deviation", y = "Mean Score")
@@
 
-#Calculate the means and standard deviations for the specified US female athletes across all apparatuses
- # Filter for USA female athletes
-  usa_female_scores <- data %>%
-  filter(Country == "USA" & Gender == "w")
+#Calculate the means and standard deviations for the specified US male athletes across all apparatuses
+ # Filter for USA male athletes
+  usa_male_scores <- data %>%
+  filter(Country == "USA" & Gender == "m")
 
   # Define the list of last names
-  target_last_names <- c("biles", "mcclain", "blakely", "sumanasekera", "jones", "carey", "chiles", "matthews", "wong", "lincoln", "dicello")
+  target_last_names <- c("juda", "young", "moldauer", "hong", "hale", "malone", "whittenburg", "loos", "bock", "walker")
 
   # Filter the data for the specified athletes
-  selected_athletes <- usa_female_scores %>%
+  selected_athletes <- usa_male_scores %>%
   filter(LastName %in% target_last_names)
@@
   # Define the list of last names
-  target_last_names <- c("biles", "mcclain", "blakely", "sumanasekera", "jones", "carey", "chiles", "matthews", "wong", "lincoln", "dicello")
+  target_last_names <- c("juda", "young", "moldauer", "hong", "hale", "malone", "whittenburg", "loos", "bock", "walker")
 
@@
   geom_text(hjust = 0, vjust = 0) +
-  labs(x = "Sum of Standard Deviations", y = "Sum of Means", title = "Female All-Around Candidates")
+  labs(x = "Sum of Standard Deviations", y = "Sum of Means", title = "Male All-Around Candidates")
 
@@
   labs(x = "Sum of Standard Deviations", y = "Mean Score") +
-  ggtitle("Top 10 Combinations of 3 Female Athletes with Highest Mean Score")
+  ggtitle("Top 10 Combinations of 3 Male Athletes with Highest Mean Score")
 
@@
   labs(x = "Sum of Standard Deviations", y = "Mean Score") +
-  ggtitle("Top 10 Combinations of 4 Female Athletes with Highest Mean Score")
+  ggtitle("Top 10 Combinations of 4 Male Athletes with Highest Mean Score")
 

### 2024-01-03 manuscript/submission.tex
moving revised text from prior repo

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{cleveref}
\hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor = blue}
\usepackage{natbib}
\usepackage{natbib}
\usepackage{float}
\usepackage{pdfpages}

\usepackage[colorlinks=true, citecolor=blue]{hyperref}

\title{UCSAS 2024 USOPC Data Challenge}
\author{Kathleen Houlihan\\
  Department of Statistics\\
  University of Connecticut
}

\begin{document}
\maketitle

\begin{abstract}
    For decades, gymnastics has been the most watched sport in the Summer Olympics and the United States 
    has been known for bringing gold medal-winning gymnasts to compete. In the 2020 
    Summer Olympics games in Tokyo, the United States female artistic gymnastics team took home 
    the gold medal in the Women's All Around, a bronze medal in the Women's Balance 
    Beam, a gold medal in the Women's Floor Exercise, a silver medal for the Women's
    Team, a bronze medal in the Women's Uneven Bars, and a silver medal in the Women's Vault. 
    Noting that the United States was the only country to have a team medal in all six women's artistic gymnastics 
    categories, the likely hood of the United States bringing female athletes that will medal in the 2024 
    Paris Olympics is very probable. However, in the 2020 Summer Olympic games in Tokyo, the United States 
    male artistic gymnastics team did not medal at all. For the purposes of this data challenge, I focused my 
    time on finding a statistical method that best isolates strong female gymnasts that would be prime candidates 
    for the 2024 olympics as the female USA team historically earns more medals than the male team. Later, I applied 
    my statistical method to the male team, which I anticipate will earn fewer medals than the female team, if any. 
    Noting that this data challenge can be interpreted in a number of ways, I designed my methods to maximize the 
    overall medal count while also placing greatest importance on the team all-around medal. In this paper, I will 
    identify which five female and male artistic gymnasts are best suited to be sent to the Paris 2024 
    Olympics on behalf of the United States in order to maximize the expected medal count.

\end{abstract}

\section{Data}
\label{sec:data}

To predict which of the United States athletes are most likely to medal on the various apparatuses, 
I will be using the cleaned data that 
is provided in the UCSAS data challenge that includes data from major domestic and international 
gymnastic competitions from 2022 and 2023. I have opted against using the data from major domestic
and international gymnastic competions from 2017 to 2021 as time, injuries, 
and other factors can have a large impact on the success of a gymnast, so the greatest predictor
of the Olympic outcomes in 2024 will be the most recent data.
\\
For the purposes of my research design, when determining the most ideal feamle olympic candidates, 
I limited the data I utilized to only include female United States
gymnasts, presuming that the United States female gymnasts have a strong chance at earning medals in any category, 
based on the results of the 2020 Summer Olympics. When determining the most ideal American male candidates, 
I did inspect the data of non United States gymnasts in order to determine which medals the United States 
male team has the greatest chance of earning. 
Furthermore, I processed the data to remove any scores of zero based on the assumption that these may 
be indicative of missing scores and that instances of these scores are rare. I further justified my decision 
to eliminate scores of zero for the purposes of knowing the true mean scores of each athlete on each 
apparatus for each successful attempt. Additionally, for some athletes and competitions, I found that the vault
apparatus was listed as "VT," "VT1," and "VT2." This discrepancy is due to the fact that athletes are permitted
two attempts on the vault apparatus. In an effort to interpret the data as accurately as possible and avoid having 
multiple statistics for one athlete on the same apparatus, I corrected this discrepancy by merging "VT," "VT1," and 
"VT2" to all be reported as "VT." Also, the data source is flawed as it alternates between reporting athlete names
in upper or lower case letters. In order to correct this, I converted all last names to lower case for consistency 
purposes. Lastly, the data source is inconsistent in the manner that it reports the first names of athletes as certain
athletes are listed using only their first name at some competitions and are listed using their first and middle names 
under the "first name" category for other competitions. In order to resolve this discrepancy, I manually verified that 
any athletes listed under two names were the same person and I further verified that there were no United States  
athletes with the same last name so that all statistical computations could be completed through grouping by last 
name alone.

\section{Methods}
\label{sec:meth}

The most important task of the larger project involves determining which 5 athletes
should be brought to the 2024 Olympics in order to maximize success. For women, this means determining 
which five athletes stand the greatest chance of winning the gold medal for the women's individual all-around,
team all-around, Balance Beam, Floor Exercise, Uneven Bars, and Vault.

In order to select the appropriate athletes, I first processed the data as described in Section~\ref{sec:data}.
Then, I calculated and examined the mean and standard deviations of each American female athlete's score 
on each apparatus. I also examined the number of observations for each athlete on each apparatus to familiarize 
myself with which athletes tend to compete at the most competitions and on which apparatuses. Then, I plotted 
the mean versus the standard deviation of the ten athletes with the highest mean scores on each apparatus. 
Using this visual, I created a parameter for each apparatus that uses both mean score and standard 
deviation to identify which athletes are best suited to be considered to compete on behalf of the United 
States on each apparatus. Using this parameter, I identified the "best" five athletes that compete on
each apparatus based on both their success, a high mean score, and their inconsistency, their standard deviation. 
In cases where there was only one observation, the standard deviation value is unavailable.
For the purposes of this research, it is reasonable to ignore any athletes who have only competed once on a particular apparatus.

Next, using only the athletes I identified as the "best" on each apparatus using the parameters, 
I calculated the sum of each athletes mean score for each apparatus and the sum of each athlete's standard 
deviation for each apparatus. Similarly to before, I plotted the mean score versus the standard deviation for 
these selected athletes. This plot is intended to represent
the United States' best candidates for earning a gold medal for the individual all-around component of the Olympics.

Then, using the sum of each selected athlete's mean score for each apparatus and the sum of each athlete's standard 
deviation for each apparatus which was previously calculated, I calculated the summed mean score and standard deviation sum 
of every combination of three athletes. Next, I plotted the summed mean score versus the standard deviation for the ten 
athlete combinations with the highest summed mean score. This plot is designed to identify the United States' best 
candidates for the all-around team finals.

Furthermore, using the sum of each selected athlete's mean score for each apparatus and the sum of each athlete's standard 
deviation for each apparatus which was previously calculated, I calculated the summed mean score and standard deviation sum 
of every combination of four athletes. Once again, I plotted the summed mean score versus the standard deviation for the ten 
athlete combinations with the highest summed mean score. This plot is designed to identify the United States' best 
candidates for the all-around team qualifying round.

Finally, in order to build a final team of five, I manually examined all of the data in an effort to include in 
the final team the best three candidates for the team all-around, the best candidate for the fourth qualifying position, 
the best two candidates for the individual all-around, and the two athletes that are superior on each apparatus.

For men, the overall statistical method I used to determine the team of five male gymnasts that should be sent 
to the 2024 Olympics was very similar, but varied when it came to determining the final fifth team member. After 
using the same method to determine the United States' best four male candidates for the team all-around qualification 
round, I calculated the mean score for every male gymnast on every apparatus in order to determine which apparatuses 
the male USA team had the greatest chance of earning medals on. From this data, there was only one additional male 
USA gymnast that ranked globally in the top ten for a particular apparatus based on mean score alone.

\section{Results}
\label{sec:res}

\begin{figure}
  \centering
  \includegraphics[scale=0.6]{FemaleAthletesBB.pdf}
  \caption{Top 10 Female Candidates for the Olympic Balance Beam Apparatus}
  \label{fig:BB}
\end{figure}

\begin{table}
  \caption{Top ten female balance beam candidates and their mean minus standard deviation parameter values}
  \label{tab:tableBBP}
\centering
\begin{tabular}[t]{lccllll}
 \toprule
Last Name & Mean minus Standard Deviation\\
\midrule
biles & 14.38228\\
\midrule
mcclain & 14.13944\\
\midrule
lee & 13.68558\\
\midrule
sumanasekera & 12.94901\\
\midrule
blakely & 12.78173\\
\midrule
jones & 12.58175\\
\midrule
roberson & 12.50378\\
\midrule
wong & 12.48469\\
\midrule
dicello & 12.44901\\
\midrule
frazier & NA\\
\bottomrule
\end{tabular}
\end{table}

Based on the plot of the top ten female athletes on the balance beam apparatus I selected the parameter of 
the score standard deviation subtracted from the mean score in order to identify the best suited five 
athletes. Based on the parameter, the five "best" female athletes on balance beam are Biles, Mcclain, 
Lee, Sumanasekera, and Blakely.

\begin{figure}
  \centering
  \includegraphics[scale=0.6]{FemaleAthletesFX.pdf}
  \caption{Top 10 Female Candidates for the Olympic Floor Exercise Apparatus}
  \label{fig:FX}
\end{figure}

\begin{table}
  \caption{Top ten female floor exercise candidates and their mean minus standard deviation parameter values}
  \label{tab:tableFXP}
\centering
\begin{tabular}[t]{lccllll}
 \toprule
Last Name & Mean minus Standard Deviation\\
\midrule
biles & 14.55017\\
\midrule
lincoln & 13.73014\\
\midrule
carey & 13.41335\\
\midrule
dicello & 13.40725\\
\midrule
chiles & 13.38463\\
\midrule
jones & 13.28955\\
\midrule
mcclain & 13.21401\\
\midrule
wong & 13.16001\\
\midrule
roberson & 12.97918\\
\midrule
frazier & NA\\
\bottomrule
\end{tabular}
\end{table}

Based on the plot of the top ten female athletes on the floor exercise apparatus I selected the parameter of 
the score standard deviation subtracted from the mean score in order to identify the best suited five 
athletes. Based on the parameter, the five "best" female athletes for floor exercise are Biles, Lincoln, Carey, 
Mcclain, Dicello, Chiles.

\begin{figure}
  \centering
  \includegraphics[scale=0.6]{FemaleAthletesUB.pdf}
  \caption{Top 10 Female Candidates for the Olympic Uneven Bar Apparatus}
  \label{fig:UB}
\end{figure}

\begin{table}
  \caption{Top 10 female uneven bars candidates and their mean minus half their standard deviation parameter values}
  \label{tab:tableUBP}
\centering
\begin{tabular}[t]{lccllll}
 \toprule
Last Name & Mean minus (0.5)Standard Deviation\\
\midrule
jones & 14.26300\\
\midrule
biles & 14.16786\\
\midrule
wong & 13.58939\\
\midrule
matthews & 13.50008\\
\midrule
blakely & 13.48821\\
\midrule
greaves & 13.47197\\
\midrule
miller & 13.37735\\
\midrule
chiles & 13.33873\\
\midrule
zhou & 13.27921\\
\midrule
walker & NA\\
\bottomrule
\end{tabular}
\end{table}

Based on the plot of the top ten female athletes on the uneven bars apparatus I selected the parameter of 
half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
athletes. Based on the parameter, the five "best" female athletes for uneven bars are Jones, Biles, Wong, 
Matthews, and Blakely.

\begin{figure}
  \centering
  \includegraphics[scale=0.6]{FemaleAthletesVT.pdf}
  \caption{Top 10 Female Candidates for the Olympic Vault Apparatus}
  \label{fig:VT}
\end{figure}

\begin{table}
  \caption{Top ten female vault candidates and their mean minus half their standard deviation parameter values}
  \label{tab:tableVTP}
\centering
\begin{tabular}[t]{lccllll}
 \toprule
Last Name & Mean minus (0.5)Standard Deviation\\
\midrule
biles & 14.77708\\
\midrule
carey & 14.35999\\
\midrule
mcclain & 14.20297\\
\midrule
jones & 14.19854\\
\midrule
chiles & 14.10796\\
\midrule
sumanasekera & 14.06650\\
\midrule
blakely & 14.05000\\
\midrule
dicello & 13.88174\\
\midrule
richardson & NA\\
\midrule
torry & NA\\
\bottomrule
\end{tabular}
\end{table}

Based on the plot of the top ten athletes on the vault apparatus I selected the parameter of 
half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
athletes. Based on the parameter, the five "best" female athletes on vault are Biles, Carey, Mcclain, Jones, 
and Chiles.

Ultimately, the list of athletes that ranked among the top five United States female athletes includes Biles, 
Mcclain, Lee, Sumanasekera, Blakely, Carey, Jones, Chiles, Wong, Matthews, Lincoln, and Dicello. However, Lee 
only has reported data for two out of four of the female apparatuses so she will not be considered with the other 
eleven athletes for individual or team all-around. Thus, the list of selected athletes that are involved in future 
computations includes Biles, Mcclain, Sumanasekera, Blakely, Carey, Jones, Chiles, Wong, Matthews, Lincoln, 
and Dicello.

\begin{figure}
  \centering
  \includegraphics[scale=0.6]{FemaleAthletesAACandidates.pdf}
  \caption{The best candidates for the female individual all-around medal}
  \label{fig:IAA}
\end{figure}

\begin{table}
  \caption{Summed means and standard deviations for the selected female individual all-around candidates}
  \label{tab:tableIAA}
\centering
\begin{tabular}[t]{lccllll}
 \toprule
Last Name & Summed Means & Summed Standard Deviations\\
\midrule
biles & 58.70640 & 1.124194\\
\midrule
jones & 55.82380 & 1.826863\\
\midrule
mcclain & 55.68333 & 1.741128\\
\midrule
blakely & 54.52908 & 2.017384\\
\midrule
chiles & 54.50832 & 1.941718\\
\midrule
carey & 54.38711 & 1.770006\\
\midrule
wong & 54.28354 & 1.936921\\
\midrule
dicello & 54.11984 & 1.958245\\
\midrule
sumanasekera & 53.15505 & 1.589704\\
\midrule
lincoln & 52.39283 & 3.048907\\
\midrule
matthews & 52.33400 & 1.556188\\
\bottomrule
\end{tabular}
\end{table}

Figure~\ref{fig:IAA} and table~\ref{tab:tableIAA} display the summed mean score and standard deviation 
for each of the eleven selected female all-around candidates.

\begin{figure}
  \centering
  \includegraphics[scale=0.6]{FemaleAthletesAA3.pdf}
  \caption{Top 10 combinations of three female candidates for the team all-around medal}
  \label{fig:AA3}
\end{figure}

\begin{table}
  \caption{The five combinations of three United States female athletes with the highest combined mean scores}
  \label{tab:tableAA3}
\centering
\begin{tabular}[t]{lccllll}
 \toprule
Combination & Combined Score & Standard Deviation Sum\\
\midrule
biles, jones, mcclain & 170.2135 & 4.692185\\
\midrule
biles, blakely, jones & 169.0593 & 4.968440\\
\midrule
biles, chiles, jones & 169.0385 & 4.892774\\
\midrule
biles, blakely, mcclain & 168.9188 & 4.882706\\
\midrule
biles, carey, jones
& 168.9173 & 4.721063
\\
\bottomrule
\end{tabular}
\end{table}

Figure~\ref{fig:AA3} and table~\ref{tab:tableAA3} display the summed mean score and standard deviation 
for the top combinations of three of the eleven selected female all-around candidates.

\begin{figure}
  \centering
  \includegraphics[scale=0.6]{FemaleAthletesAA4.pdf}
  \caption{Top 10 combinations of four female candidates for the team all-around medal}
  \label{fig:AA4}
\end{figure}

\begin{table}
  \caption{The five combinations of four United States female athletes with the highest combined mean scores}
  \label{tab:tableAA4}
\centering
\begin{tabular}[t]{lccllll}
 \toprule
Combination & Combined Score & Standard Deviation Sum\\
\midrule
biles, blakely, jones, mcclain & 224.7426 & 6.709569\\
\midrule
biles, chiles, jones, mcclain & 224.7218 & 6.633903\\
\midrule
biles, carey, jones, mcclain & 224.6006 & 6.462191\\
\midrule
biles, jones, mcclain, wong & 224.4971 & 6.629105\\
\midrule
biles, dicello, jones, mcclain & 224.3334 & 6.650430\\
\bottomrule
\end{tabular}
\end{table}

Figure~\ref{fig:AA4} and table~\ref{tab:tableAA4} display the summed mean score and standard deviation 
for the top combinations of four of the eleven selected all-around candidates.

\begin{figure}
    \centering
    \includegraphics[scale=0.6]{MaleAthletesFX.pdf}
    \caption{Top 10 Male Candidates for the Olympic Floor Exercise Apparatus}
    \label{fig:FXM}
  \end{figure}

  Based on the plot of the top ten male athletes on the floor exercise apparatus I selected the parameter of 
  the score standard deviation subtracted from the mean score in order to identify the best suited five 
  athletes. Based on the parameter, the five "best" male athletes on floor exercise are Juda, Mccool, Young, Moldauer, 
  and Hong.

\begin{figure}
    \centering
    \includegraphics[scale=0.6]{MaleAthletesVT.pdf}
    \caption{Top 10 Male Candidates for the Olympic Vault Apparatus}
    \label{fig:VTM}
  \end{figure}

  Based on the plot of the top ten male athletes on the vault apparatus I selected the parameter of 
  the score standard deviation subtracted from the mean score in order to identify the best suited five 
  athletes. Based on the parameter, the five "best" male athletes on vault are Hale, Young, Malone, Briones, and 
  Juda.

\begin{figure}
    \centering
    \includegraphics[scale=0.6]{MaleAthletesSR.pdf}
    \caption{Top 10 Male Candidates for the Olympic Still Rings Apparatus}
    \label{fig:SRM}
  \end{figure}

  Based on the plot of the top ten male athletes on the still rings apparatus I selected the parameter of 
  half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
  athletes. Based on the parameter, the five "best" male athletes on still rings are Whittenburg, Briones, Diab, 
  Hong, and Loos.

\begin{figure}
    \centering
    \includegraphics[scale=0.6]{MaleAthletesPH.pdf}
    \caption{Top 10 Male Candidates for the Olympic Pommel Horse Apparatus}
    \label{fig:PHM}
  \end{figure}

  Based on the plot of the top ten male athletes on the pommel horse apparatus I selected the parameter of 
  half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
  athletes. Based on the parameter, the five "best" male athletes on pommel horse are Nedoroscik, Young, Malone, 
  Dang, and Bock.

\begin{figure}
    \centering
    \includegraphics[scale=0.6]{MaleAthletesPB.pdf}
    \caption{Top 10 Male Candidates for the Olympic Parallel Bars Apparatus}
    \label{fig:PBM}
  \end{figure}

  Based on the plot of the top ten male athletes on the parallel bars apparatus I selected the parameter of 
  half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
  athletes. Based on the parameter, the five "best" male athletes on parallel bars are Hong, Chou, Walker, Malone, 
  and Phillips.

\begin{figure}
    \centering
    \includegraphics[scale=0.6]{MaleAthletesHB.pdf}
    \caption{Top 10 Male Candidates for the Olympic High Bar Apparatus}
    \label{fig:HBM}
  \end{figure}

  Based on the plot of the top ten male athletes on the high bar apparatus I selected the parameter of 
  half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
  athletes. Based on the parameter, the five "best" male athletes on high bar are Malone, Juda, Briones, Bold, and 
  Nguyen.

  Ultimately, the list of athletes that ranked among the top five United States male athletes 19 distinct 
  names. However, nine of these athletes have not competed on all six apparatuses, so they will not be considered 
  with the other ten athletes for individual or team all-around. Thus, the list of selected athletes that 
  are involved in future computations includes Juda, Young, Moldauer, Hong, Hale, Malone, Whittenburg, Loos, 
  Bock, and Walker.

\begin{figure}
    \centering
    \includegraphics[scale=0.6]{MaleAthletesAACandidates.pdf}
    \caption{The best candidates for the male individual all-around medal}
    \label{fig:IAAM}
  \end{figure}

  Figure~\ref{fig:IAAM} displays the summed mean score and standard deviation 
  for each of the ten selected male all-around candidates.

\begin{figure}
    \centering
    \includegraphics[scale=0.6]{MaleAthletesAA3.pdf}
    \caption{Top 10 combinations of three male candidates for the team all-around medal}
    \label{fig:MAA3}
  \end{figure}

  Figure~\ref{fig:MAA3} displays the summed mean score and standard deviation 
  for the top combinations of three of the ten selected male all-around candidates.

  \begin{figure}
    \centering
    \includegraphics[scale=0.6]{MaleAthletesAA4.pdf}
    \caption{Top 10 combinations of four male candidates for the team all-around medal}
    \label{fig:MAA4}
  \end{figure}

  Figure~\ref{fig:MAA4} displays the summed mean score and standard deviation 
  for the top combinations of four of the ten selected male all-around candidates.

\section{Discussion}
\label{sec:dis}

In my preliminary steps, I calculated the mean and standard deviation for every female athlete on each 
apparatus they were reported to have competed on. From these calculations, I decided to cut out most athletes 
by only inspecting athletes that ranked in the top ten by mean score alone for each apparatus. This was a 
reasonable elimination of data as the score values among the top ten candidates varied enough, often by over a 
full point, to justify that athletes that never ranked in the top ten for a particular apparatus are not 
competitive enough to medal at the Olympics.

I later developed a parameter for each apparatus to further reduce the list of athletes to only include athletes 
that rank in the top five for each apparatus. However, I designed the parameters to be dependent on the score 
standard deviation in addition to the mean score. The intent of the paramter is to create a frontier that selects 
athletes that have high mean scores and low standard deviations in order to select athletes that are the most 
successful and consistent. Ultimately, for each apparatus I selcted the five athletes with highest parameter value.

For the blanace beam apparatus, I selected the parameter: mean score minus standard deviation. This parameter 
is very reasonable as it selects athletes with high means and low standard deviations first (Biles then Mcclain 
then Lee) and selects athletes with lower standard deviations when means are similar (Sumanasekera then Blakely).

For the floor exercise apparatus, I selected the parameter: mean score minus standard deviation. This parameter 
is reasonable as well as it selects athletes with high means and low standard deviations first (Biles then Lincoln) 
and selects athletes with lower standard deviations when means are similar (Carey, Dicello, and Chiles). Note, the 
order in which Carey, Dicello, and Chiles "should" be selected is debatable, but it is most important that the 
parameter selected these athletes as opposed to athletes that have similar mean scores but higher standard deviations 
(Jones and Mcclain) or low standard deviations and low low mean scores (Wong).

For the uneven bars apparatus, I selected the parameter: mean score minus half of the standard deviation. 
This parameter is reasonable as well as it selects athletes with extremely high means first (Jones then Biles) and selects 
athletes with lower standard deviations when means are similar (Wong then Matthews then Blakely).

For the vault apparatus, I selected the parameter: mean score minus half of the standard deviation. 
This parameter is reasonable as well as it selects athletes with extremely high means first (Biles then Carey) and selects 
athletes with lower standard deviations when means are similar (Mcclain then Jones then Chiles).

Then, I used these candidates in order to determine who is best suited to compete in the all-around events. 
First, I calculted the summed mean score and summed standard deviation for each selected athlete. Looking at the data 
values and plot of these individual all-around candidates, it is very clear that Biles is strong candidate to 
compete for the individual all-around medal. However, it is not clear whether Jones or Mcclain is better suited 
to be the second United States individual all-around candidate.

Then, I used the summed mean score and summed standard deviation for each selected athlete to calculate the 
summed mean score and summed standard deviation for every combination of 
three and four of these selected athletes. Looking at the data values and plot of the combinations of three athletes, 
it is clear that Biles, Jones, and Mcclain are by far the best suited trio to compete for the team all-around medal. 
Additionally, since this data suggests that both Mcclain and Jones should compete in the qualifying round, there 
is no need to select one over the other for the second individual all-around candidate spot as they would both get 
the opportunity to qualify, and their scores at the Olympics will determine which athlete, if either, will qualify 
to attend the individual all-around finals.

Looking at the data values and plot of the combinations of four athletes, it is not clear whether Chiles, Carey, or 
Blakely is best suited to be the fourth team all-around candidate as their means and standard deviations are very 
similar. However, looking at the individual apparatus events provides justification for who to ultimately select. 
Knowing that two athletes per country can compete for an apparatus medal, it is strategic to try to compose the 
team of the best two United States athletes for each apparatus. Based on the computations and plots, the superior two 
athletes on balance beam are Biles and Mcclain, the superior two athletes on floor exercise are Biles and Lincoln, 
the superior two athletes on uneven bars are Jones and Biles, and the superior two athletes on vault are Biles 
and Carey. Since Lincoln was not among our top candidates for an all-around medal, it would be logical to select her 
as the fifth United States Olympic team member who does not compete in the all-around qualifying round. Additionally, 
since Carey is one of the candidates being considering for the all-around qualifying round and she is one of our superior 
athletes on vault, it is reasonable to also select her to be the final member of the Olympic team. Although, the 
summed combination that included Carey has the lowest mean in comparison to the combinations including Chiles or 
Blakely, the selection of Carey can be further justified by the facts that the summed mean score difference is 
within one point the combination including Carey has the lowest summed standard deviation.

Ultimately, in order to maximize the the number of medals the Unites States female team wins, I would comprise the 
team of the athletes Biles, Jones, Mcclain, Lincoln, and Carey.

Similarly, I used the same method to determine the "best" male all-around candidates as I did for females. From 
Figure~\ref{fig:IAAM} I determined that Juda and Malone are the best male Individual all-around candidates. From 
Figure~\ref{fig:MAA3} I determined that Juda, Malone, and Young are the best male team all-around finalists 
candidates. Additionally, from Figure~\ref{fig:MAA4} I determined that Moldauer is the best candidate to also compete 
with Juda, Malone, and Young in the all-around qualifying round. Comparatively, determining the "best" fifth Olympic 
teammate is challenging as there are several apparatuses where our "best" competitor is not among the four 
previously selected teammates. However, through examining the the mean score for every male gymnast on every apparatus 
we can see that many of our "best" candidates are still ranked very poorly globally, and therefore would not have a 
strong liklihood of medalling at the olympics. Among all of the male USA athletes that are not yet selected, the only 
athlete that has a relatively decent chance of medaling is Hale, who ranks 6th globally for the Vault apparatus.

Ultimately, in order to maximize the the number of medals the Unites States male team wins, I would comprise the 
team of the athletes Juda, Malone, Young, Moldauer, and Hale.

\end{document}

### 2024-01-09 code/codeprocessfemale.Rmd
uploading updated male and female code process files

@@
 library(readr)
+library(cowplot)
 ```
@@
 # Read the CSV file
-data <- read.csv("../KH-UCSAS-Submission/gym2024data/cleandata/data_2022_2023.csv", header = TRUE)
+data <- read.csv("../gym2024data/cleandata/data_2022_2023.csv", header = TRUE)
 
@@
 
-  # Plot each apparatus on separate graphs
+  # Plot each apparatus on one graph
   for (apparatus in unique(top_10_athletes$Apparatus)) {
   data_subset <- filter(top_10_athletes, Apparatus == apparatus)
-  p <- ggplot(data_subset, aes(x = SD_Score, y = Mean_Score, label = LastName)) +
+  p <- ggplot(top_10_athletes, aes(x = SD_Score, y = Mean_Score, label = LastName)) +
   geom_point() +
   geom_text(hjust = 0, vjust = 0) +
-    labs(title = paste("Top 10 Female Athletes in", apparatus),
-         x = "Standard Deviation", y = "Mean Score")
+  labs(title = "Top 10 Female Athletes",
+       x = "Standard Deviation", y = "Mean Score") +
+  facet_wrap(~Apparatus, scales = "free") +
+  theme_minimal()
+  }
+
+  # Print the combined plot
   print(p)
-  }
 
@@
   # Create a scatter plot
-  p <- ggplot(sums, aes(x = Sum_SD, y = Sum_Means, label = LastName)) +
+  p1 <- ggplot(sums, aes(x = Sum_SD, y = Sum_Means, label = LastName)) +
   geom_point() +
@@
   # Display the plot
-  print(p)
+  print(p1)
 
@@
   # Create a scatter plot for the top 10 combinations
-  p <- ggplot(top_10_combinations, aes(x = SD_Sum, y = Mean_Score)) +
+  p2 <- ggplot(top_10_combinations, aes(x = SD_Sum, y = Mean_Score)) +
   geom_point() +
@@
   labs(x = "Sum of Standard Deviations", y = "Mean Score") +
-  ggtitle("Top 10 Combinations of 3 Female Athletes with Highest Mean Score")
+  ggtitle("Combinations of 3 Female Athletes")
 
   # Display the plot
-  print(p)
+  print(p2)
 
@@
   # Create a scatter plot for the top 10 combinations
-  p <- ggplot(top_10_combinations_4, aes(x = SD_Sum, y = Mean_Score)) +
+  p3 <- ggplot(top_10_combinations_4, aes(x = SD_Sum, y = Mean_Score)) +
   geom_point() +
@@
   labs(x = "Sum of Standard Deviations", y = "Mean Score") +
-  ggtitle("Top 10 Combinations of 4 Female Athletes with Highest Mean Score")
+  ggtitle("Combinations of 4 Female Athletes")
 
   # Display the plot
-  print(p)
+  print(p3)
+
+  # Combine the three plots into one three-panel plot
+  combined_plot <- cowplot::plot_grid(p1, p2, p3, ncol = 1)
+
+  # Print the combined plot
+  print(combined_plot)
 ```

### 2024-01-09 code/codeprocessmale.Rmd
uploading updated male and female code process files

@@
 
-  # Plot each apparatus on separate graphs
+  # Plot each apparatus on one graph
   for (apparatus in unique(top_10_athletes$Apparatus)) {
   data_subset <- filter(top_10_athletes, Apparatus == apparatus)
-  p <- ggplot(data_subset, aes(x = SD_Score, y = Mean_Score, label = LastName)) +
+  p <- ggplot(top_10_athletes, aes(x = SD_Score, y = Mean_Score, label = LastName)) +
   geom_point() +
   geom_text(hjust = 0, vjust = 0) +
-    labs(title = paste("Top 10 Male Athletes in", apparatus),
-         x = "Standard Deviation", y = "Mean Score")
+  labs(x = "Standard Deviation", y = "Mean Score") +
+  facet_wrap(~Apparatus, scales = "free") +
+  theme_minimal()
   print(p)
@@
   # Display the plot
-  print(p)
+  print(p2)
 
@@
   # Display the plot
-  print(p)
+  print(p3)
+
+  # Combine the three plots into one three-panel plot
+  combined_plot <- cowplot::plot_grid(p1, p2, p3, ncol = 1)
+
+  # Print the combined plot
+  print(combined_plot)
 ```

### 2024-01-09 manuscript/submission.tex
altering title, hyperref error, bib source
adding major figure changes for both men and women

@@
 
-\usepackage[colorlinks=true, citecolor=blue]{hyperref}
-
-\title{UCSAS 2024 USOPC Data Challenge}
+\title{Predicting The Success of The Female United States Artistic Gymnastics Team at The 2024 Paris Olympics 
+Using Mean and Standard Deviation Derived Parameters}
 \author{Kathleen Houlihan\\
@@
 \begin{abstract}
+
+\end{abstract}
+
+\section{Introduction}
+\label{sec:intro}
+
 For decades, gymnastics has been the most watched sport in the Summer Olympics and the United States 
@@
 
-\end{abstract}
+Currently there is no literature available relevant to predicting gymnastics outcomes at the 2024 
+Paris Summer Olympics or at recent olympics. However, there is literature that relates to various aspects of 
+the data that will be used to form my predictions. For example, the article 'The Prediction of All-Around 
+Event Final Score Based On D and E Score Factors In Women's Artistic Gymnastics' aims to determine the 
+impact of individual apparatus difficulty and execution scores on overall score. 
+Expertise from this article could be useful in allowing us to understand how D and E scores, 
+which are available in my data, play an effort in predicting the overall score. Additionally, the paper 
+'Performance rating in men’s world elite artistic gymnastics: a status-quo study on scoring 
+tendencies at Olympic Games following rule changes' also can play a similar role in predicting overall 
+score. This paper's objective is to analyze the effect on elite artistic gymnastics had by the 2006 rule change 
+which aimed to reduce the dominance of difficulty while strengthening performance differentiation in 
+competition. Notably, the paper found that the rule change resulted in significantly enhanced performance 
+differentiation with the execution or E score being the main predictor of the final score as opposed to 
+the difficulty or D score. Furthermore, in the article 'How Apparatus Difficulty Scores Affect All 
+Around Results in Men's Artistic Gymnastics,' the authors use regression, cluster, and ANOVA analysis to 
+analyze how difficulty scores predict overall score differently across different apparatuses. However, in this 
+article the authors found that while difficulty scores may have predictive tendancies for some apparatuses, 
+the strength of the prediction varied drastically from apparatus to apparatus, with there being little to no 
+predictive ability for some apparatuses. Ultimately, the available literature on predicting artistic 
+gymnastic scores seemed generally limited to how we can use the E and D scores provided in the data sets 
+to predict overall score, but some aspects of this literature casted doubt on whether E and D scores should be 
+used as predictors at all.
 
@@
 apparatus for each successful attempt. Additionally, for some athletes and competitions, I found that the vault
-apparatus was listed as "VT," "VT1," and "VT2." This discrepancy is due to the fact that athletes are permitted
+apparatus was listed as 'VT,' 'VT1,' and 'VT2.' This discrepancy is due to the fact that athletes are permitted
 two attempts on the vault apparatus. In an effort to interpret the data as accurately as possible and avoid having 
-multiple statistics for one athlete on the same apparatus, I corrected this discrepancy by merging "VT," "VT1," and 
-"VT2" to all be reported as "VT." Also, the data source is flawed as it alternates between reporting athlete names
+multiple statistics for one athlete on the same apparatus, I corrected this discrepancy by merging 'VT,' 'VT1,' and 
+'VT2' to all be reported as 'VT.' Also, the data source is flawed as it alternates between reporting athlete names
 in upper or lower case letters. In order to correct this, I converted all last names to lower case for consistency 
@@
 athletes are listed using only their first name at some competitions and are listed using their first and middle names 
-under the "first name" category for other competitions. In order to resolve this discrepancy, I manually verified that 
+under the 'first name' category for other competitions. In order to resolve this discrepancy, I manually verified that 
 any athletes listed under two names were the same person and I further verified that there were no United States  
@@
 deviation to identify which athletes are best suited to be considered to compete on behalf of the United 
-States on each apparatus. Using this parameter, I identified the "best" five athletes that compete on
+States on each apparatus. Using this parameter, I identified the 'best' five athletes that compete on
 each apparatus based on both their success, a high mean score, and their inconsistency, their standard deviation. 
@@
 
-Next, using only the athletes I identified as the "best" on each apparatus using the parameters, 
+Next, using only the athletes I identified as the 'best' on each apparatus using the parameters, 
 I calculated the sum of each athletes mean score for each apparatus and the sum of each athlete's standard 
@@
   \centering
-  \includegraphics[scale=0.6]{FemaleAthletesBB.pdf}
-  \caption{Top 10 Female Candidates for the Olympic Balance Beam Apparatus}
-  \label{fig:BB}
+  \includegraphics[scale=0.7]{FemaleAthleteApparatus.pdf}
+  \caption{Top 10 Female Candidates for the Olympic Balance Beam, Floor Exercise, Uneven Bars, and Vault Apparatus}
+  \label{fig:FA}
 \end{figure}
@@
 \begin{table}
-  \caption{Top ten female balance beam candidates and their mean minus standard deviation parameter values}
+  \caption{Top ten female candidates for each apparatus based on mean score alone and 
+  their $\mu - \alpha \sigma$ parameter values}
   \label{tab:tableBBP}
 \centering
-\begin{tabular}[t]{lccllll}
+\begin{tabular}[t]{llllllll}
  \toprule
-Last Name & Mean minus Standard Deviation\\
+  \multicolumn{2}{c}{BB} & \multicolumn{2}{c}{FX} & \multicolumn{2}{c}{UB} & \multicolumn{2}{c}{VT}\\
+  \cmidrule(lr){1-2}\cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
+Athlete & $\mu - \sigma$ & Athlete & $\mu - \sigma$ & Athlete & $\mu - 0.5 \sigma$ & Athlete & $\mu - 0.5 \sigma$\\
 \midrule
-biles & 14.38228\\
+biles & 14.38 & biles & 14.55 & jones & 14.26 & Biles & 14.78\\
 \midrule
-mcclain & 14.13944\\
+mcclain & 14.14 & lincoln & 13.73 & biles & 14.17 & Carey & 14.36\\
 \midrule
-lee & 13.68558\\
+lee & 13.69 & carey & 13.41 & wong & 13.59 & Mcclain & 14.20\\
 \midrule
-sumanasekera & 12.94901\\
+sumanasekera & 12.95 & dicello & 13.4 & matthews & 13.50 & Jones & 14.20\\
 \midrule
-blakely & 12.78173\\
+blakely & 12.78 & chiles & 13.38 & blakely & 13.49 & Chiles & 14.11\\
 \midrule
-jones & 12.58175\\
+jones & 12.58 & jones & 13.29 & greaves & 13.47 & sumanasekera & 14.07\\
 \midrule
-roberson & 12.50378\\
+roberson & 12.50 & mcclain & 13.21 & miller & 13.38 & blakely & 14.05\\
 \midrule
-wong & 12.48469\\
+wong & 12.48 & wong & 13.16 & chiles & 13.34 & dicello & 13.88\\
 \midrule
-dicello & 12.44901\\
+dicello & 12.45 & roberson & 12.98 & zhou & 13.28 & richardson & NA\\
 \midrule
-frazier & NA\\
+frazier & NA & frazier & NA & walker & NA & torry & NA\\
 \bottomrule
@@
 the score standard deviation subtracted from the mean score in order to identify the best suited five 
-athletes. Based on the parameter, the five "best" female athletes on balance beam are Biles, Mcclain, 
+athletes. Based on the parameter, the five 'best' female athletes on balance beam are Biles, Mcclain, 
 Lee, Sumanasekera, and Blakely.
-
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.6]{FemaleAthletesFX.pdf}
-  \caption{Top 10 Female Candidates for the Olympic Floor Exercise Apparatus}
-  \label{fig:FX}
-\end{figure}
-
-\begin{table}
-  \caption{Top ten female floor exercise candidates and their mean minus standard deviation parameter values}
-  \label{tab:tableFXP}
-\centering
-\begin{tabular}[t]{lccllll}
- \toprule
-Last Name & Mean minus Standard Deviation\\
-\midrule
-biles & 14.55017\\
-\midrule
-lincoln & 13.73014\\
-\midrule
-carey & 13.41335\\
-\midrule
-dicello & 13.40725\\
-\midrule
-chiles & 13.38463\\
-\midrule
-jones & 13.28955\\
-\midrule
-mcclain & 13.21401\\
-\midrule
-wong & 13.16001\\
-\midrule
-roberson & 12.97918\\
-\midrule
-frazier & NA\\
-\bottomrule
-\end{tabular}
-\end{table}
 
@@
 the score standard deviation subtracted from the mean score in order to identify the best suited five 
-athletes. Based on the parameter, the five "best" female athletes for floor exercise are Biles, Lincoln, Carey, 
+athletes. Based on the parameter, the five 'best' female athletes for floor exercise are Biles, Lincoln, Carey, 
 Mcclain, Dicello, Chiles.
-
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.6]{FemaleAthletesUB.pdf}
-  \caption{Top 10 Female Candidates for the Olympic Uneven Bar Apparatus}
-  \label{fig:UB}
-\end{figure}
-
-\begin{table}
-  \caption{Top 10 female uneven bars candidates and their mean minus half their standard deviation parameter values}
-  \label{tab:tableUBP}
-\centering
-\begin{tabular}[t]{lccllll}
- \toprule
-Last Name & Mean minus (0.5)Standard Deviation\\
-\midrule
-jones & 14.26300\\
-\midrule
-biles & 14.16786\\
-\midrule
-wong & 13.58939\\
-\midrule
-matthews & 13.50008\\
-\midrule
-blakely & 13.48821\\
-\midrule
-greaves & 13.47197\\
-\midrule
-miller & 13.37735\\
-\midrule
-chiles & 13.33873\\
-\midrule
-zhou & 13.27921\\
-\midrule
-walker & NA\\
-\bottomrule
-\end{tabular}
-\end{table}
 
@@
 half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-athletes. Based on the parameter, the five "best" female athletes for uneven bars are Jones, Biles, Wong, 
+athletes. Based on the parameter, the five 'best' female athletes for uneven bars are Jones, Biles, Wong, 
 Matthews, and Blakely.
-
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.6]{FemaleAthletesVT.pdf}
-  \caption{Top 10 Female Candidates for the Olympic Vault Apparatus}
-  \label{fig:VT}
-\end{figure}
-
-\begin{table}
-  \caption{Top ten female vault candidates and their mean minus half their standard deviation parameter values}
-  \label{tab:tableVTP}
-\centering
-\begin{tabular}[t]{lccllll}
- \toprule
-Last Name & Mean minus (0.5)Standard Deviation\\
-\midrule
-biles & 14.77708\\
-\midrule
-carey & 14.35999\\
-\midrule
-mcclain & 14.20297\\
-\midrule
-jones & 14.19854\\
-\midrule
-chiles & 14.10796\\
-\midrule
-sumanasekera & 14.06650\\
-\midrule
-blakely & 14.05000\\
-\midrule
-dicello & 13.88174\\
-\midrule
-richardson & NA\\
-\midrule
-torry & NA\\
-\bottomrule
-\end{tabular}
-\end{table}
 
@@
 half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-athletes. Based on the parameter, the five "best" female athletes on vault are Biles, Carey, Mcclain, Jones, 
+athletes. Based on the parameter, the five 'best' female athletes on vault are Biles, Carey, Mcclain, Jones, 
 and Chiles.
@@
   \centering
-  \includegraphics[scale=0.6]{FemaleAthletesAACandidates.pdf}
-  \caption{The best candidates for the female individual all-around medal}
-  \label{fig:IAA}
+  \includegraphics[scale=0.55]{FemaleMultipleAllAround.pdf}
+  \caption{The best candidates for the female individual all-around and team all around medals}
+  \label{fig:FAA}
 \end{figure}
-
-\begin{table}
-  \caption{Summed means and standard deviations for the selected female individual all-around candidates}
-  \label{tab:tableIAA}
-\centering
-\begin{tabular}[t]{lccllll}
- \toprule
-Last Name & Summed Means & Summed Standard Deviations\\
-\midrule
-biles & 58.70640 & 1.124194\\
-\midrule
-jones & 55.82380 & 1.826863\\
-\midrule
-mcclain & 55.68333 & 1.741128\\
-\midrule
-blakely & 54.52908 & 2.017384\\
-\midrule
-chiles & 54.50832 & 1.941718\\
-\midrule
-carey & 54.38711 & 1.770006\\
-\midrule
-wong & 54.28354 & 1.936921\\
-\midrule
-dicello & 54.11984 & 1.958245\\
-\midrule
-sumanasekera & 53.15505 & 1.589704\\
-\midrule
-lincoln & 52.39283 & 3.048907\\
-\midrule
-matthews & 52.33400 & 1.556188\\
-\bottomrule
-\end{tabular}
-\end{table}
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.6]{FemaleAthletesAA3.pdf}
-  \caption{Top 10 combinations of three female candidates for the team all-around medal}
-  \label{fig:AA3}
-\end{figure}
-
-\begin{table}
-  \caption{The five combinations of three United States female athletes with the highest combined mean scores}
-  \label{tab:tableAA3}
-\centering
-\begin{tabular}[t]{lccllll}
- \toprule
-Combination & Combined Score & Standard Deviation Sum\\
-\midrule
-biles, jones, mcclain & 170.2135 & 4.692185\\
-\midrule
-biles, blakely, jones & 169.0593 & 4.968440\\
-\midrule
-biles, chiles, jones & 169.0385 & 4.892774\\
-\midrule
-biles, blakely, mcclain & 168.9188 & 4.882706\\
-\midrule
-biles, carey, jones
-& 168.9173 & 4.721063
-\\
-\bottomrule
-\end{tabular}
-\end{table}
-
 Figure~\ref{fig:AA3} and table~\ref{tab:tableAA3} display the summed mean score and standard deviation 
 for the top combinations of three of the eleven selected female all-around candidates.
-
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.6]{FemaleAthletesAA4.pdf}
-  \caption{Top 10 combinations of four female candidates for the team all-around medal}
-  \label{fig:AA4}
-\end{figure}
-
-\begin{table}
-  \caption{The five combinations of four United States female athletes with the highest combined mean scores}
-  \label{tab:tableAA4}
-\centering
-\begin{tabular}[t]{lccllll}
- \toprule
-Combination & Combined Score & Standard Deviation Sum\\
-\midrule
-biles, blakely, jones, mcclain & 224.7426 & 6.709569\\
-\midrule
-biles, chiles, jones, mcclain & 224.7218 & 6.633903\\
-\midrule
-biles, carey, jones, mcclain & 224.6006 & 6.462191\\
-\midrule
-biles, jones, mcclain, wong & 224.4971 & 6.629105\\
-\midrule
-biles, dicello, jones, mcclain & 224.3334 & 6.650430\\
-\bottomrule
-\end{tabular}
-\end{table}
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.6]{MaleAthletesFX.pdf}
-    \caption{Top 10 Male Candidates for the Olympic Floor Exercise Apparatus}
-    \label{fig:FXM}
-  \end{figure}
-
   Based on the plot of the top ten male athletes on the floor exercise apparatus I selected the parameter of 
   the score standard deviation subtracted from the mean score in order to identify the best suited five 
-  athletes. Based on the parameter, the five "best" male athletes on floor exercise are Juda, Mccool, Young, Moldauer, 
+  athletes. Based on the parameter, the five 'best' male athletes on floor exercise are Juda, Mccool, Young, Moldauer, 
   and Hong.
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.6]{MaleAthletesVT.pdf}
-    \caption{Top 10 Male Candidates for the Olympic Vault Apparatus}
-    \label{fig:VTM}
-  \end{figure}
 
@@
   the score standard deviation subtracted from the mean score in order to identify the best suited five 
-  athletes. Based on the parameter, the five "best" male athletes on vault are Hale, Young, Malone, Briones, and 
+  athletes. Based on the parameter, the five 'best' male athletes on vault are Hale, Young, Malone, Briones, and 
   Juda.
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.6]{MaleAthletesSR.pdf}
-    \caption{Top 10 Male Candidates for the Olympic Still Rings Apparatus}
-    \label{fig:SRM}
-  \end{figure}
 
@@
   half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-  athletes. Based on the parameter, the five "best" male athletes on still rings are Whittenburg, Briones, Diab, 
+  athletes. Based on the parameter, the five 'best' male athletes on still rings are Whittenburg, Briones, Diab, 
   Hong, and Loos.
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.6]{MaleAthletesPH.pdf}
-    \caption{Top 10 Male Candidates for the Olympic Pommel Horse Apparatus}
-    \label{fig:PHM}
-  \end{figure}
 
@@
   half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-  athletes. Based on the parameter, the five "best" male athletes on pommel horse are Nedoroscik, Young, Malone, 
+  athletes. Based on the parameter, the five 'best' male athletes on pommel horse are Nedoroscik, Young, Malone, 
   Dang, and Bock.
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.6]{MaleAthletesPB.pdf}
-    \caption{Top 10 Male Candidates for the Olympic Parallel Bars Apparatus}
-    \label{fig:PBM}
-  \end{figure}
 
@@
   half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-  athletes. Based on the parameter, the five "best" male athletes on parallel bars are Hong, Chou, Walker, Malone, 
+  athletes. Based on the parameter, the five 'best' male athletes on parallel bars are Hong, Chou, Walker, Malone, 
   and Phillips.
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.6]{MaleAthletesHB.pdf}
-    \caption{Top 10 Male Candidates for the Olympic High Bar Apparatus}
-    \label{fig:HBM}
-  \end{figure}
 
@@
   half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-  athletes. Based on the parameter, the five "best" male athletes on high bar are Malone, Juda, Briones, Bold, and 
+  athletes. Based on the parameter, the five 'best' male athletes on high bar are Malone, Juda, Briones, Bold, and 
   Nguyen.
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.6]{MaleAthletesAACandidates.pdf}
-    \caption{The best candidates for the male individual all-around medal}
-    \label{fig:IAAM}
-  \end{figure}
-
   Figure~\ref{fig:IAAM} displays the summed mean score and standard deviation 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.6]{MaleAthletesAA3.pdf}
-    \caption{Top 10 combinations of three male candidates for the team all-around medal}
-    \label{fig:MAA3}
-  \end{figure}
-
   Figure~\ref{fig:MAA3} displays the summed mean score and standard deviation 
   for the top combinations of three of the ten selected male all-around candidates.
-
-  \begin{figure}
-    \centering
-    \includegraphics[scale=0.6]{MaleAthletesAA4.pdf}
-    \caption{Top 10 combinations of four male candidates for the team all-around medal}
-    \label{fig:MAA4}
-  \end{figure}
 
@@
 and selects athletes with lower standard deviations when means are similar (Carey, Dicello, and Chiles). Note, the 
-order in which Carey, Dicello, and Chiles "should" be selected is debatable, but it is most important that the 
+order in which Carey, Dicello, and Chiles 'should' be selected is debatable, but it is most important that the 
 parameter selected these athletes as opposed to athletes that have similar mean scores but higher standard deviations 
@@
 
-Similarly, I used the same method to determine the "best" male all-around candidates as I did for females. From 
+\appendix
+
+\section{Appendix: Application of the Mean and Standard Deviation Derived Parameters Methods For The Male 
+United States Artistic Gymnastics Team at The 2024 Paris Olympics}
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.5]{MaleAthleteApparatus.pdf}
+  \caption{Top 10 Male Candidates for the Olympic Floor Exercise, Pommel Horse, Still Rings, Vault, Parallel Bars, 
+  and High Bar Apparatus}
+  \label{fig:FA}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.7]{MaleMultipleAllAround.pdf}
+  \caption{The best candidates for the male individual all-around and team all around medals}
+  \label{fig:FAA}
+\end{figure}
+
+Similar to the female model, I used the same method to determine the 'best' male all-around candidates as I did for females. From 
 Figure~\ref{fig:IAAM} I determined that Juda and Malone are the best male Individual all-around candidates. From 
@@
 candidates. Additionally, from Figure~\ref{fig:MAA4} I determined that Moldauer is the best candidate to also compete 
-with Juda, Malone, and Young in the all-around qualifying round. Comparatively, determining the "best" fifth Olympic 
-teammate is challenging as there are several apparatuses where our "best" competitor is not among the four 
+with Juda, Malone, and Young in the all-around qualifying round. Comparatively, determining the 'best' fifth Olympic 
+teammate is challenging as there are several apparatuses where our 'best' competitor is not among the four 
 previously selected teammates. However, through examining the the mean score for every male gymnast on every apparatus 
-we can see that many of our "best" candidates are still ranked very poorly globally, and therefore would not have a 
+we can see that many of our 'best' candidates are still ranked very poorly globally, and therefore would not have a 
 strong liklihood of medalling at the olympics. Among all of the male USA athletes that are not yet selected, the only 
@@
 
+\bibliographystyle{chicago}
+\bibliography{citations}
+
 \end{document}

### 2024-01-09 manuscript/submission.tex
updating abstract outline

@@
 
+NOT DONE
+
 \begin{document}
@@
 \begin{abstract}
+
+  Open with a sentence to establish the importance of the subject of the paper.
+  Identify a gap in the literature to set up the background of the paper.
+  Highlight the novelty/contributions of the paper.
+  For application papers, allude to new discoveries and their impacts.
+  For method papers, outline the essence of the methodology, and evidence from theoretical and numerical studies supporting the methods.
+  It must make sense when read in isolation for those who only read the abstract, and must also provide a clear and accurate summary of the manuscript for readers who read the entire manuscript (Zeiger 2000).
 

### 2024-01-09 manuscript/submission.tex
testing quotation revision

@@
 apparatus for each successful attempt. Additionally, for some athletes and competitions, I found that the vault
-apparatus was listed as 'VT,' 'VT1,' and 'VT2.' This discrepancy is due to the fact that athletes are permitted
+apparatus was listed as `VT,` `VT1,` and 'VT2.' This discrepancy is due to the fact that athletes are permitted
 two attempts on the vault apparatus. In an effort to interpret the data as accurately as possible and avoid having 

### 2024-01-09 manuscript/submission.tex
resolving quotation mark errors

@@
 Paris Summer Olympics or at recent olympics. However, there is literature that relates to various aspects of 
-the data that will be used to form my predictions. For example, the article 'The Prediction of All-Around 
-Event Final Score Based On D and E Score Factors In Women's Artistic Gymnastics' aims to determine the 
+the data that will be used to form my predictions. For example, the article ``The Prediction of All-Around 
+Event Final Score Based On D and E Score Factors In Women's Artistic Gymnastics'' aims to determine the 
 impact of individual apparatus difficulty and execution scores on overall score. 
@@
 which are available in my data, play an effort in predicting the overall score. Additionally, the paper 
-'Performance rating in men’s world elite artistic gymnastics: a status-quo study on scoring 
-tendencies at Olympic Games following rule changes' also can play a similar role in predicting overall 
+``Performance rating in men’s world elite artistic gymnastics: a status-quo study on scoring 
+tendencies at Olympic Games following rule changes'' also can play a similar role in predicting overall 
 score. This paper's objective is to analyze the effect on elite artistic gymnastics had by the 2006 rule change 
@@
 differentiation with the execution or E score being the main predictor of the final score as opposed to 
-the difficulty or D score. Furthermore, in the article 'How Apparatus Difficulty Scores Affect All 
-Around Results in Men's Artistic Gymnastics,' the authors use regression, cluster, and ANOVA analysis to 
+the difficulty or D score. Furthermore, in the article ``How Apparatus Difficulty Scores Affect All 
+Around Results in Men's Artistic Gymnastics,'' the authors use regression, cluster, and ANOVA analysis to 
 analyze how difficulty scores predict overall score differently across different apparatuses. However, in this 
@@
 apparatus for each successful attempt. Additionally, for some athletes and competitions, I found that the vault
-apparatus was listed as `VT,` `VT1,` and 'VT2.' This discrepancy is due to the fact that athletes are permitted
+apparatus was listed as ``VT,'' ``VT1,'' and ``VT2.'' This discrepancy is due to the fact that athletes are permitted
 two attempts on the vault apparatus. In an effort to interpret the data as accurately as possible and avoid having 
-multiple statistics for one athlete on the same apparatus, I corrected this discrepancy by merging 'VT,' 'VT1,' and 
-'VT2' to all be reported as 'VT.' Also, the data source is flawed as it alternates between reporting athlete names
+multiple statistics for one athlete on the same apparatus, I corrected this discrepancy by merging ``VT,'' ``VT1,'' and 
+``VT2'' to all be reported as ``VT.'' Also, the data source is flawed as it alternates between reporting athlete names
 in upper or lower case letters. In order to correct this, I converted all last names to lower case for consistency 
@@
 athletes are listed using only their first name at some competitions and are listed using their first and middle names 
-under the 'first name' category for other competitions. In order to resolve this discrepancy, I manually verified that 
+under the ``first name'' category for other competitions. In order to resolve this discrepancy, I manually verified that 
 any athletes listed under two names were the same person and I further verified that there were no United States  
@@
 deviation to identify which athletes are best suited to be considered to compete on behalf of the United 
-States on each apparatus. Using this parameter, I identified the 'best' five athletes that compete on
+States on each apparatus. Using this parameter, I identified the ``best'' five athletes that compete on
 each apparatus based on both their success, a high mean score, and their inconsistency, their standard deviation. 
@@
 
-Next, using only the athletes I identified as the 'best' on each apparatus using the parameters, 
+Next, using only the athletes I identified as the ``best'' on each apparatus using the parameters, 
 I calculated the sum of each athletes mean score for each apparatus and the sum of each athlete's standard 
@@
 the score standard deviation subtracted from the mean score in order to identify the best suited five 
-athletes. Based on the parameter, the five 'best' female athletes on balance beam are Biles, Mcclain, 
+athletes. Based on the parameter, the five ``best'' female athletes on balance beam are Biles, Mcclain, 
 Lee, Sumanasekera, and Blakely.
@@
 the score standard deviation subtracted from the mean score in order to identify the best suited five 
-athletes. Based on the parameter, the five 'best' female athletes for floor exercise are Biles, Lincoln, Carey, 
+athletes. Based on the parameter, the five ``best'' female athletes for floor exercise are Biles, Lincoln, Carey, 
 Mcclain, Dicello, Chiles.
@@
 half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-athletes. Based on the parameter, the five 'best' female athletes for uneven bars are Jones, Biles, Wong, 
+athletes. Based on the parameter, the five ``best'' female athletes for uneven bars are Jones, Biles, Wong, 
 Matthews, and Blakely.
@@
 half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-athletes. Based on the parameter, the five 'best' female athletes on vault are Biles, Carey, Mcclain, Jones, 
+athletes. Based on the parameter, the five ``best'' female athletes on vault are Biles, Carey, Mcclain, Jones, 
 and Chiles.
@@
   the score standard deviation subtracted from the mean score in order to identify the best suited five 
-  athletes. Based on the parameter, the five 'best' male athletes on floor exercise are Juda, Mccool, Young, Moldauer, 
+  athletes. Based on the parameter, the five ``best'' male athletes on floor exercise are Juda, Mccool, Young, Moldauer, 
   and Hong.
@@
   the score standard deviation subtracted from the mean score in order to identify the best suited five 
-  athletes. Based on the parameter, the five 'best' male athletes on vault are Hale, Young, Malone, Briones, and 
+  athletes. Based on the parameter, the five ``best'' male athletes on vault are Hale, Young, Malone, Briones, and 
   Juda.
@@
   half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-  athletes. Based on the parameter, the five 'best' male athletes on still rings are Whittenburg, Briones, Diab, 
+  athletes. Based on the parameter, the five ``best'' male athletes on still rings are Whittenburg, Briones, Diab, 
   Hong, and Loos.
@@
   half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-  athletes. Based on the parameter, the five 'best' male athletes on pommel horse are Nedoroscik, Young, Malone, 
+  athletes. Based on the parameter, the five ``best'' male athletes on pommel horse are Nedoroscik, Young, Malone, 
   Dang, and Bock.
@@
   half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-  athletes. Based on the parameter, the five 'best' male athletes on parallel bars are Hong, Chou, Walker, Malone, 
+  athletes. Based on the parameter, the five ``best'' male athletes on parallel bars are Hong, Chou, Walker, Malone, 
   and Phillips.
@@
   half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-  athletes. Based on the parameter, the five 'best' male athletes on high bar are Malone, Juda, Briones, Bold, and 
+  athletes. Based on the parameter, the five ``best'' male athletes on high bar are Malone, Juda, Briones, Bold, and 
   Nguyen.
@@
 and selects athletes with lower standard deviations when means are similar (Carey, Dicello, and Chiles). Note, the 
-order in which Carey, Dicello, and Chiles 'should' be selected is debatable, but it is most important that the 
+order in which Carey, Dicello, and Chiles ``should'' be selected is debatable, but it is most important that the 
 parameter selected these athletes as opposed to athletes that have similar mean scores but higher standard deviations 
@@
 
-Similar to the female model, I used the same method to determine the 'best' male all-around candidates as I did for females. From 
+Similar to the female model, I used the same method to determine the ``best'' male all-around candidates as I did for females. From 
 Figure~\ref{fig:IAAM} I determined that Juda and Malone are the best male Individual all-around candidates. From 
@@
 candidates. Additionally, from Figure~\ref{fig:MAA4} I determined that Moldauer is the best candidate to also compete 
-with Juda, Malone, and Young in the all-around qualifying round. Comparatively, determining the 'best' fifth Olympic 
-teammate is challenging as there are several apparatuses where our 'best' competitor is not among the four 
+with Juda, Malone, and Young in the all-around qualifying round. Comparatively, determining the ``best'' fifth Olympic 
+teammate is challenging as there are several apparatuses where our ``best'' competitor is not among the four 
 previously selected teammates. However, through examining the the mean score for every male gymnast on every apparatus 
-we can see that many of our 'best' candidates are still ranked very poorly globally, and therefore would not have a 
+we can see that many of our ``best'' candidates are still ranked very poorly globally, and therefore would not have a 
 strong liklihood of medalling at the olympics. Among all of the male USA athletes that are not yet selected, the only 

### 2024-01-10 manuscript/submission.tex
committing recent changes to the abstract, introduction, and data section based on the professor's statistical writing notes

@@
 
-NOT DONE
-
 \begin{document}
@@
 
-  Open with a sentence to establish the importance of the subject of the paper.
-  Identify a gap in the literature to set up the background of the paper.
-  Highlight the novelty/contributions of the paper.
-  For application papers, allude to new discoveries and their impacts.
-  For method papers, outline the essence of the methodology, and evidence from theoretical and numerical studies supporting the methods.
-  It must make sense when read in isolation for those who only read the abstract, and must also provide a clear and accurate summary of the manuscript for readers who read the entire manuscript (Zeiger 2000).
+  Following the 2020 Toyko Olympics where the United States was the only country to have a team medal 
+  in all six of the women's artistic gymnastic events, the performance of the United States women's artistic 
+  gymnastics team at the 2024 Paris Summer Olympics is once again predicted to be the most watched Olympic 
+  dicipline both in the United States and globally. With the whole world anticipating the success of the United 
+  States women's team, it is crucial that the team of five women that are selected to represent the United States 
+  are the athletes best suited to optimize success and maximize the expected medal count in Paris 2024. As there 
+  are no preexisting statistical papers that methodize the selection of athletes for Olympic Gymnastic teams, 
+  this paper aims to answer the question of what metric should be used to judge the olympic canidacy of USA 
+  gymnasts and to outline a statistical method that can be used presently and in the future to select the ``best'' 
+  gymnasts to comprise the United States women's Olympic team in order to maximize success. Using an anatlytical 
+  method dependent on mean and standard deviation derived parameters, this paper outlines a procedure for identifying 
+  the group of five athletes who will enable the Team USA Olympic Women’s Artistic Gymnastics team to optimize 
+  success through numberically evaluating each USA athlete based on both their accuracy and precision in order to 
+  more accurately identify the ``best'' team candidates. Through application of this analytical method to present 
+  USA female artistic gymnasts, Simone Biles, Shilese Jones, Konnor McClain, Kaliya Lincoln, and Jade Carey can be 
+  identified as the the group of five athletes who will enable the Team USA Olympic Women’s Artistic Gymnastics 
+  teams to optimize success at the 2024 Paris Summer Olympics.
 
@@
 
-For decades, gymnastics has been the most watched sport in the Summer Olympics and the United States 
-has been known for bringing gold medal-winning gymnasts to compete. In the 2020 
-Summer Olympics games in Tokyo, the United States female artistic gymnastics team took home 
-the gold medal in the Women's All Around, a bronze medal in the Women's Balance 
-Beam, a gold medal in the Women's Floor Exercise, a silver medal for the Women's
-Team, a bronze medal in the Women's Uneven Bars, and a silver medal in the Women's Vault. 
-Noting that the United States was the only country to have a team medal in all six women's artistic gymnastics 
-categories, the likely hood of the United States bringing female athletes that will medal in the 2024 
-Paris Olympics is very probable. However, in the 2020 Summer Olympic games in Tokyo, the United States 
-male artistic gymnastics team did not medal at all. For the purposes of this data challenge, I focused my 
-time on finding a statistical method that best isolates strong female gymnasts that would be prime candidates 
-for the 2024 olympics as the female USA team historically earns more medals than the male team. Later, I applied 
-my statistical method to the male team, which I anticipate will earn fewer medals than the female team, if any. 
-Noting that this data challenge can be interpreted in a number of ways, I designed my methods to maximize the 
-overall medal count while also placing greatest importance on the team all-around medal. In this paper, I will 
-identify which five female and male artistic gymnasts are best suited to be sent to the Paris 2024 
-Olympics on behalf of the United States in order to maximize the expected medal count.
+At the Summer Olympics in Paris in 2024, ninety-six men and ninety-six women from around the world will 
+represent their countries and compete in the artistic gymnatics dicipline. The overall importance of the Olympics 
+cannot be understated as the games are a symbol of peaceful global interaction and give people hope that a better 
+world is possible. For decades, gymnastics has been the most watched sport in the Summer Olympics and the United 
+States has been known for bringing gold medal-winning gymnasts to compete. In the 2020 
+Summer Olympics games in Tokyo, the United States women's artistic gymnastics team was the only team to take 
+home a medal in all six categories. Hence, the likelihood of the USA Olympic Women’s Artistic Gymnastics 
+team bringing female athletes that will medal in the 2024 Paris Olympics is very probable. 
+However, in the 2020 Summer Olympic games, the United States 
+male artistic gymnastics team did not medal at all. As the female USA team historically earns more medals than 
+the male team, the focus of this paper is aimed at identifying a method that best isolates strong female gymnasts 
+that would be prime candidates for the 2024 and future Olympics. Later in this paper, the designed statistical 
+method is applied to the male team, which is anticipated to earn fewer medals than the female team, if any 
+(see Appendix). Noting that Olympic ``success'' can be interpreted in a number of ways, the methods of this 
+paper are designed to maximize the overall medal count by maximizing the USA team's opportrunities to medal in each 
+category while also placing greatest importance on the team all-around medal.
+
+\\
 
@@
 impact of individual apparatus difficulty and execution scores on overall score. 
-Expertise from this article could be useful in allowing us to understand how D and E scores, 
-which are available in my data, play an effort in predicting the overall score. Additionally, the paper 
+Expertise from this article could be useful in allowing us to understand how difficulty and execution scores 
+play a role in predicting the overall score. Additionally, the paper 
 ``Performance rating in men’s world elite artistic gymnastics: a status-quo study on scoring 
 tendencies at Olympic Games following rule changes'' also can play a similar role in predicting overall 
-score. This paper's objective is to analyze the effect on elite artistic gymnastics had by the 2006 rule change 
-which aimed to reduce the dominance of difficulty while strengthening performance differentiation in 
-competition. Notably, the paper found that the rule change resulted in significantly enhanced performance 
-differentiation with the execution or E score being the main predictor of the final score as opposed to 
-the difficulty or D score. Furthermore, in the article ``How Apparatus Difficulty Scores Affect All 
+score. Notably, the paper found that recent Olympic rule changes resulted in significantly enhanced performance 
+differentiation with the execution score being the main predictor of the final score. 
+Furthermore, in the article ``How Apparatus Difficulty Scores Affect All 
 Around Results in Men's Artistic Gymnastics,'' the authors use regression, cluster, and ANOVA analysis to 
@@
 predictive ability for some apparatuses. Ultimately, the available literature on predicting artistic 
-gymnastic scores seemed generally limited to how we can use the E and D scores provided in the data sets 
-to predict overall score, but some aspects of this literature casted doubt on whether E and D scores should be 
+gymnastic scores seemed generally limited to how difficulty and execution scores predict overall score, 
+but some aspects of this literature casts doubt on whether difficulty and execution scores should be 
 used as predictors at all.
+
+\\
+
+As existing literature fails to suggest how data from major domestic and international gymnastics competitions 
+from the seasons leading up to the Summer Olympics can be used to identify the ``best'' Olympic team candidates, 
+the analytical method presented in this paper aims to outline a procedure that takes into account data from recent 
+gymnastics competitions and Olympic competition structure in orer to identify the group of five athletes who will 
+enable the Team USA Olympic Women’s Artistic Gymnastics team to optimize success in Paris 2024. If Olympic 
+competition structure and recent competitive scores on each apparatus are taken into consideration, then an 
+anatlytical method dependent on mean and standard deviation derived parameters can be used to identify the foremost 
+candidates to compete on behalf of the United States at the Olympics.
+
+\\
+
+The rest of this paper is organized as follows. First, I will evaluate the data that is available in order to complete 
+this project in Section~\ref{sec:data}. Then, I will discuss my 
+analytical methods to determine the atheltes that should be sent to the Olympics from the United States 
+in Section~\ref{sec:meth}. Later, I will present the results of my 
+methods in Section~\ref{sec:res}. Lastly, I will discuss the meaning of my results, some challenges, 
+and some limitations of this project in Section~\ref{sec:dis}.
 
@@
 To predict which of the United States athletes are most likely to medal on the various apparatuses, 
-I will be using the cleaned data that 
-is provided in the UCSAS data challenge that includes data from major domestic and international 
-gymnastic competitions from 2022 and 2023. I have opted against using the data from major domestic
-and international gymnastic competions from 2017 to 2021 as time, injuries, 
+I will be using the cleaned data that is provided by the UConn Sports Analytics Symposium data challenge 
+that includes data from major domestic and international gymnastic competitions from 2022 and 2023. 
+I have opted against using the older data from 2017 to 2021 as time, injuries, 
 and other factors can have a large impact on the success of a gymnast, so the greatest predictor
@@
 gymnasts, presuming that the United States female gymnasts have a strong chance at earning medals in any category, 
-based on the results of the 2020 Summer Olympics. When determining the most ideal American male candidates, 
-I did inspect the data of non United States gymnasts in order to determine which medals the United States 
-male team has the greatest chance of earning. 
+based on the results of the 2020 Summer Olympics. 
 Furthermore, I processed the data to remove any scores of zero based on the assumption that these may 
@@
 
+When determining the most ideal American male candidates, 
+I did inspect the data of non United States gymnasts in order to determine which medals the United States 
+male team has the greatest chance of earning.
+
 Similar to the female model, I used the same method to determine the ``best'' male all-around candidates as I did for females. From 

### 2024-01-10 manuscript/submission.tex
converting methods section to a numbered list

@@
 of the Olympic outcomes in 2024 will be the most recent data.
+
 \\
-For the purposes of my research design, when determining the most ideal feamle olympic candidates, 
-I limited the data I utilized to only include female United States
-gymnasts, presuming that the United States female gymnasts have a strong chance at earning medals in any category, 
-based on the results of the 2020 Summer Olympics. 
-Furthermore, I processed the data to remove any scores of zero based on the assumption that these may 
-be indicative of missing scores and that instances of these scores are rare. I further justified my decision 
-to eliminate scores of zero for the purposes of knowing the true mean scores of each athlete on each 
-apparatus for each successful attempt. Additionally, for some athletes and competitions, I found that the vault
-apparatus was listed as ``VT,'' ``VT1,'' and ``VT2.'' This discrepancy is due to the fact that athletes are permitted
+
+For the purposes of this research design, when determining the most ideal feamle olympic candidates, 
+only data on female United States gymnasts is analyzed, presuming that the United States 
+female gymnasts have a strong chance at earning medals in any category, based on the results of the 2020 Summer Olympics. 
+However, several data processing steps are required to correct several inconsistencies in the data source prior to 
+analytical computations being performed.
+First, the data is processed to remove any scores of zero based on the assumption that these may 
+be indicative of missing scores and that instances of these scores are rare. The decision to eliminate scores of 
+zero is further justified for the purposes of knowing the true mean scores of each athlete on each 
+apparatus for each successful attempt. Additionally, for some athletes and competitions vault
+scores are reported as ``VT,'' ``VT1,'' and ``VT2.'' This discrepancy is due to the fact that athletes are permitted
 two attempts on the vault apparatus. In an effort to interpret the data as accurately as possible and avoid having 
-multiple statistics for one athlete on the same apparatus, I corrected this discrepancy by merging ``VT,'' ``VT1,'' and 
+multiple statistics for one athlete on the same apparatus, this discrepency is corrected by merging ``VT,'' ``VT1,'' and 
 ``VT2'' to all be reported as ``VT.'' Also, the data source is flawed as it alternates between reporting athlete names
-in upper or lower case letters. In order to correct this, I converted all last names to lower case for consistency 
+in upper or lower case letters. In order to correct this, all last names are converted to lower case for consistency 
 purposes. Lastly, the data source is inconsistent in the manner that it reports the first names of athletes as certain
 athletes are listed using only their first name at some competitions and are listed using their first and middle names 
-under the ``first name'' category for other competitions. In order to resolve this discrepancy, I manually verified that 
-any athletes listed under two names were the same person and I further verified that there were no United States  
+under the ``first name'' category for other competitions. In order to resolve this discrepancy, manual verification was used
+to ensure that any athletes listed under two names were the same person and that there were no United States  
 athletes with the same last name so that all statistical computations could be completed through grouping by last 
@@
 
-The most important task of the larger project involves determining which 5 athletes
-should be brought to the 2024 Olympics in order to maximize success. For women, this means determining 
+For women, the data challenge presents the task of determining 
 which five athletes stand the greatest chance of winning the gold medal for the women's individual all-around,
@@
 
-In order to select the appropriate athletes, I first processed the data as described in Section~\ref{sec:data}.
-Then, I calculated and examined the mean and standard deviations of each American female athlete's score 
-on each apparatus. I also examined the number of observations for each athlete on each apparatus to familiarize 
-myself with which athletes tend to compete at the most competitions and on which apparatuses. Then, I plotted 
-the mean versus the standard deviation of the ten athletes with the highest mean scores on each apparatus. 
-Using this visual, I created a parameter for each apparatus that uses both mean score and standard 
-deviation to identify which athletes are best suited to be considered to compete on behalf of the United 
-States on each apparatus. Using this parameter, I identified the ``best'' five athletes that compete on
-each apparatus based on both their success, a high mean score, and their inconsistency, their standard deviation. 
 In cases where there was only one observation, the standard deviation value is unavailable.
@@
 
-Next, using only the athletes I identified as the ``best'' on each apparatus using the parameters, 
-I calculated the sum of each athletes mean score for each apparatus and the sum of each athlete's standard 
-deviation for each apparatus. Similarly to before, I plotted the mean score versus the standard deviation for 
-these selected athletes. This plot is intended to represent
-the United States' best candidates for earning a gold medal for the individual all-around component of the Olympics.
+In order to select the appropriate athletes, I first processed the data as described in Section~\ref{sec:data} 
+and then adhered to the following procedure:
 
-Then, using the sum of each selected athlete's mean score for each apparatus and the sum of each athlete's standard 
-deviation for each apparatus which was previously calculated, I calculated the summed mean score and standard deviation sum 
-of every combination of three athletes. Next, I plotted the summed mean score versus the standard deviation for the ten 
-athlete combinations with the highest summed mean score. This plot is designed to identify the United States' best 
-candidates for the all-around team finals.
-
-Furthermore, using the sum of each selected athlete's mean score for each apparatus and the sum of each athlete's standard 
-deviation for each apparatus which was previously calculated, I calculated the summed mean score and standard deviation sum 
-of every combination of four athletes. Once again, I plotted the summed mean score versus the standard deviation for the ten 
-athlete combinations with the highest summed mean score. This plot is designed to identify the United States' best 
-candidates for the all-around team qualifying round.
-
-Finally, in order to build a final team of five, I manually examined all of the data in an effort to include in 
+\begin{enumerate}
+  \item Calculate and examine the mean and standard deviations of each American female athlete's score 
+  on each apparatus.
+  \item Calculate the number of observations for each athlete on each apparatus.
+  \item Plot the mean versus the standard deviation of the ten athletes with the highest mean scores on each 
+  apparatus.
+  \begin{enumerate}
+    \item Use these plots as a visual to represent the possible scores that could be achielved in each apparatus 
+    component of the Olympics.
+    \item Using the plots, create a parameter for each apparatus that uses both mean score and standard 
+    deviation to identify which athletes are best suited to be considered to compete on behalf of the United 
+    States on each apparatus.
+    \begin{enumerate}
+      \item Select the five athletes with the highest parameter value for each apparatus to identify the ``best'' 
+      five athletes that compete on each apparatus based on both their success, a high mean score, and their 
+      inconsistency, their standard deviation.
+    \end{enumerate}
+    \item Identify the athletes with the two largest paramter values as the ``best'' on each apparatus.
+  \end{enumerate}
+  \item Produce a list of ``target athletes'' for furture computations that contains all athletes that were identified 
+  as being in the top five for any apparatus in the last step.
+  \begin{enumerate}
+    \item Remove any athletes from the ``target athletes'' list that have not competed on all aparatuses.
+  \end{enumerate}
+  \item Calculate the sum of each ``target athlete's'' mean score for each apparatus and the sum of each athlete's standard 
+  deviation for each apparatus.
+  \item Plot the mean score sum versus the standard deviation sum for each ``target athlete.''
+  \begin{enumerate}
+    \item Use this plot as a visual to represent the possible scores that could be achielved in the individual all-around 
+    component of the Olympics.
+  \end{enumerate}
+  \item Calculate the summed mean score and standard deviation sum of every combination of three athletes using the previously 
+  calculated sum of each ``target athlete's'' mean score for each apparatus and the sum of each athlete's standard 
+  deviation for each apparatus.
+  \item Plot the summed mean score versus the standard deviation for the ten combinations of three athletes with the 
+  highest summed mean score.
+  \begin{enumerate}
+    \item Use this plot as a visual to represent the possible scores that could be achielved in the all-around team finals 
+   component of the Olympics.
+  \end{enumerate}
+  \item Calculate the summed mean score and standard deviation sum of every combination of four athletes using the previously 
+  calculated sum of each ``target athlete's'' mean score for each apparatus and the sum of each athlete's standard 
+  deviation for each apparatus.
+  \item Plot the summed mean score versus the standard deviation for the ten combinations of four athletes with the 
+  highest summed mean score.
+  \begin{enumerate}
+    \item Use this plot as a visual to represent the possible scores that could be achielved in the all-around team qualifying  
+   round of the Olympics.
+  \end{enumerate}
+  \item Visully exammine each produced plot to build a final team of five in an effort to include in 
   the final team the best three candidates for the team all-around, the best candidate for the fourth qualifying position, 
@@
 
-For men, the overall statistical method I used to determine the team of five male gymnasts that should be sent 
-to the 2024 Olympics was very similar, but varied when it came to determining the final fifth team member. After 
-using the same method to determine the United States' best four male candidates for the team all-around qualification 
-round, I calculated the mean score for every male gymnast on every apparatus in order to determine which apparatuses 
-the male USA team had the greatest chance of earning medals on. From this data, there was only one additional male 
-USA gymnast that ranked globally in the top ten for a particular apparatus based on mean score alone.
+\end{enumerate}
 
@@
 
+For men, the overall statistical method I used to determine the team of five male gymnasts that should be sent 
+to the 2024 Olympics was very similar, but varied when it came to determining the final fifth team member. After 
+using the same method to determine the United States' best four male candidates for the team all-around qualification 
+round, I calculated the mean score for every male gymnast on every apparatus in order to determine which apparatuses 
+the male USA team had the greatest chance of earning medals on. From this data, there was only one additional male 
+USA gymnast that ranked globally in the top ten for a particular apparatus based on mean score alone.
+
 When determining the most ideal American male candidates, 

### 2024-01-10 manuscript/submission.tex
cleaning up results section to only include figures and necessary references to figures

@@
 
-In cases where there was only one observation, the standard deviation value is unavailable.
-For the purposes of this research, it is reasonable to ignore any athletes who have only competed once on a particular apparatus.
+In order to reduce the vast list of United States female gymnasts to just five athletes, the proposed method in 
+this paper utilizes a paramter value of the score standard deviation multipled by some alpha value subtracted 
+from the mean score for each apparatus, or $\mu - \alpha \sigma$. This paramter value serves to rank athletes based 
+on having both a high mean score for a particualr event and low standard deviation. By subtracting the standard deviation 
+from the mean score, we are able to identify the ``best'' athletes as having the highest parameter values. 
+This alpha value is decided by examining the plots of the mean versus the standard deviation of the ten athletes 
+with the highest mean scores on each apparatus. The default alpha value is 1, and ideally this produces a parameter 
+value where the athletes with the highest mean scores and lowest standard deviations have the highest parameter values. 
+However, in cases where the rank produced by the parameter value selects athletes with comparatively low mean scores and 
+low standrad deviations prior to athletes with significantly higher mean scores and slightly high standard deviations, 
+this alpha value should be reduced until the rank of the athletes coordinates with the order that seems visually most 
+logical based on the plots. While the parameters are to an extent subjective, in the final analysis the exact rank that 
+is determined by the parameter is not terribly signifiant as the parameter values are used to determine the top five 
+athletes for each apparatus and typically play the largest role in determining which athletes are included at the margin. 
+Ultimately, if an athlete is bordering being 4th, 5th, 6th, or 7th best for a particualr apparatus in the United States 
+and the athlete is not superior on another apparatus, it is highly unlikely that they would be selected for the Olympic 
+team at all. In cases where an athlete only has one observation for a prticular apparatus, the 
+standard deviation value is unavailable and thus the parameter value cannot be calculated. For the purposes of this 
+research, it is reasonable to ignore any athletes who have only competed once on a particular apparatus as they would 
+likely not be selected to compete on that apparatus at the Olympics.
 
@@
 
-Based on the plot of the top ten female athletes on the balance beam apparatus I selected the parameter of 
+Based on the plot of the top ten female athletes on the balance beam apparatus in figure~\ref{fig:FA} I selected the parameter of 
 the score standard deviation subtracted from the mean score in order to identify the best suited five 
-athletes. Based on the parameter, the five ``best'' female athletes on balance beam are Biles, Mcclain, 
-Lee, Sumanasekera, and Blakely.
-
-Based on the plot of the top ten female athletes on the floor exercise apparatus I selected the parameter of 
-the score standard deviation subtracted from the mean score in order to identify the best suited five 
-athletes. Based on the parameter, the five ``best'' female athletes for floor exercise are Biles, Lincoln, Carey, 
-Mcclain, Dicello, Chiles.
-
-Based on the plot of the top ten female athletes on the uneven bars apparatus I selected the parameter of 
+athletes. Based on the parameter displayed in table~\ref[tablebbp], the five ``best'' female athletes on balance beam are Biles, Mcclain, 
+Lee, Sumanasekera, and Blakely with Biles and McClain being expert for this apparatus. Simialrly, the five ``best'' 
+female athletes for floor exercise are Biles, Lincoln, Carey, 
+Mcclain, Dicello, Chiles with Biles and Lincoln being expert for this apparatus. Based on the plot of the top ten 
+female athletes on the uneven bars apparatus I selected the parameter of 
 half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
 athletes. Based on the parameter, the five ``best'' female athletes for uneven bars are Jones, Biles, Wong, 
-Matthews, and Blakely.
-
-Based on the plot of the top ten athletes on the vault apparatus I selected the parameter of 
-half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-athletes. Based on the parameter, the five ``best'' female athletes on vault are Biles, Carey, Mcclain, Jones, 
-and Chiles.
+Matthews, and Blakely with Jones and Biles being expert for this apparatus. Similarly, the five ``best'' female 
+athletes on vault are Biles, Carey, Mcclain, Jones, 
+and Chiles with Biles and Carey being expert for this apparatus.
 
@@
 only has reported data for two out of four of the female apparatuses so she will not be considered with the other 
-eleven athletes for individual or team all-around. Thus, the list of selected athletes that are involved in future 
-computations includes Biles, Mcclain, Sumanasekera, Blakely, Carey, Jones, Chiles, Wong, Matthews, Lincoln, 
-and Dicello.
+eleven athletes for individual or team all-around.
 
@@
 
-Figure~\ref{fig:IAA} and table~\ref{tab:tableIAA} display the summed mean score and standard deviation 
-for each of the eleven selected female all-around candidates.
-
-Figure~\ref{fig:AA3} and table~\ref{tab:tableAA3} display the summed mean score and standard deviation 
-for the top combinations of three of the eleven selected female all-around candidates.
-
-Figure~\ref{fig:AA4} and table~\ref{tab:tableAA4} display the summed mean score and standard deviation 
-for the top combinations of four of the eleven selected all-around candidates.
-
-  Based on the plot of the top ten male athletes on the floor exercise apparatus I selected the parameter of 
-  the score standard deviation subtracted from the mean score in order to identify the best suited five 
-  athletes. Based on the parameter, the five ``best'' male athletes on floor exercise are Juda, Mccool, Young, Moldauer, 
-  and Hong.
-
-  Based on the plot of the top ten male athletes on the vault apparatus I selected the parameter of 
-  the score standard deviation subtracted from the mean score in order to identify the best suited five 
-  athletes. Based on the parameter, the five ``best'' male athletes on vault are Hale, Young, Malone, Briones, and 
-  Juda.
-
-  Based on the plot of the top ten male athletes on the still rings apparatus I selected the parameter of 
-  half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-  athletes. Based on the parameter, the five ``best'' male athletes on still rings are Whittenburg, Briones, Diab, 
-  Hong, and Loos.
-
-  Based on the plot of the top ten male athletes on the pommel horse apparatus I selected the parameter of 
-  half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-  athletes. Based on the parameter, the five ``best'' male athletes on pommel horse are Nedoroscik, Young, Malone, 
-  Dang, and Bock.
-
-  Based on the plot of the top ten male athletes on the parallel bars apparatus I selected the parameter of 
-  half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-  athletes. Based on the parameter, the five ``best'' male athletes on parallel bars are Hong, Chou, Walker, Malone, 
-  and Phillips.
-
-  Based on the plot of the top ten male athletes on the high bar apparatus I selected the parameter of 
-  half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-  athletes. Based on the parameter, the five ``best'' male athletes on high bar are Malone, Juda, Briones, Bold, and 
-  Nguyen.
-
-  Ultimately, the list of athletes that ranked among the top five United States male athletes 19 distinct 
-  names. However, nine of these athletes have not competed on all six apparatuses, so they will not be considered 
-  with the other ten athletes for individual or team all-around. Thus, the list of selected athletes that 
-  are involved in future computations includes Juda, Young, Moldauer, Hong, Hale, Malone, Whittenburg, Loos, 
-  Bock, and Walker.
-
-  Figure~\ref{fig:IAAM} displays the summed mean score and standard deviation 
-  for each of the ten selected male all-around candidates.
-
-  Figure~\ref{fig:MAA3} displays the summed mean score and standard deviation 
-  for the top combinations of three of the ten selected male all-around candidates.
-
-  Figure~\ref{fig:MAA4} displays the summed mean score and standard deviation 
-  for the top combinations of four of the ten selected male all-around candidates.
-
-\section{Discussion}
-\label{sec:dis}
-
-In my preliminary steps, I calculated the mean and standard deviation for every female athlete on each 
-apparatus they were reported to have competed on. From these calculations, I decided to cut out most athletes 
-by only inspecting athletes that ranked in the top ten by mean score alone for each apparatus. This was a 
-reasonable elimination of data as the score values among the top ten candidates varied enough, often by over a 
-full point, to justify that athletes that never ranked in the top ten for a particular apparatus are not 
-competitive enough to medal at the Olympics.
-
-I later developed a parameter for each apparatus to further reduce the list of athletes to only include athletes 
-that rank in the top five for each apparatus. However, I designed the parameters to be dependent on the score 
-standard deviation in addition to the mean score. The intent of the paramter is to create a frontier that selects 
-athletes that have high mean scores and low standard deviations in order to select athletes that are the most 
-successful and consistent. Ultimately, for each apparatus I selcted the five athletes with highest parameter value.
-
-For the blanace beam apparatus, I selected the parameter: mean score minus standard deviation. This parameter 
-is very reasonable as it selects athletes with high means and low standard deviations first (Biles then Mcclain 
-then Lee) and selects athletes with lower standard deviations when means are similar (Sumanasekera then Blakely).
-
-For the floor exercise apparatus, I selected the parameter: mean score minus standard deviation. This parameter 
-is reasonable as well as it selects athletes with high means and low standard deviations first (Biles then Lincoln) 
-and selects athletes with lower standard deviations when means are similar (Carey, Dicello, and Chiles). Note, the 
-order in which Carey, Dicello, and Chiles ``should'' be selected is debatable, but it is most important that the 
-parameter selected these athletes as opposed to athletes that have similar mean scores but higher standard deviations 
-(Jones and Mcclain) or low standard deviations and low low mean scores (Wong).
-
-For the uneven bars apparatus, I selected the parameter: mean score minus half of the standard deviation. 
-This parameter is reasonable as well as it selects athletes with extremely high means first (Jones then Biles) and selects 
-athletes with lower standard deviations when means are similar (Wong then Matthews then Blakely).
-
-For the vault apparatus, I selected the parameter: mean score minus half of the standard deviation. 
-This parameter is reasonable as well as it selects athletes with extremely high means first (Biles then Carey) and selects 
-athletes with lower standard deviations when means are similar (Mcclain then Jones then Chiles).
-
-Then, I used these candidates in order to determine who is best suited to compete in the all-around events. 
-First, I calculted the summed mean score and summed standard deviation for each selected athlete. Looking at the data 
-values and plot of these individual all-around candidates, it is very clear that Biles is strong candidate to 
+Based on the plots in figure~\ref{fig:FAA}, it is very clear that Biles is strong candidate to 
 compete for the individual all-around medal. However, it is not clear whether Jones or Mcclain is better suited 
-to be the second United States individual all-around candidate.
-
-Then, I used the summed mean score and summed standard deviation for each selected athlete to calculate the 
-summed mean score and summed standard deviation for every combination of 
-three and four of these selected athletes. Looking at the data values and plot of the combinations of three athletes, 
+to be the second United States individual all-around candidate. Looking at the data values and plot of the combinations of three athletes, 
 it is clear that Biles, Jones, and Mcclain are by far the best suited trio to compete for the team all-around medal. 
@@
 the opportunity to qualify, and their scores at the Olympics will determine which athlete, if either, will qualify 
-to attend the individual all-around finals.
-
-Looking at the data values and plot of the combinations of four athletes, it is not clear whether Chiles, Carey, or 
+to attend the individual all-around finals. Looking at plot of the combinations of four athletes, it is not clear whether Chiles, Carey, or 
 Blakely is best suited to be the fourth team all-around candidate as their means and standard deviations are very 
@@
 
-Ultimately, in order to maximize the the number of medals the Unites States female team wins, I would comprise the 
-team of the athletes Biles, Jones, Mcclain, Lincoln, and Carey.
+Hence, based on the proposed method, in order to maximize the number of medals the Unites States female team wins, 
+the team should be comprised of the athletes Biles, Jones, Mcclain, Lincoln, and Carey.
+
+\section{Discussion}
+\label{sec:dis}
+
+In my preliminary steps, I calculated the mean and standard deviation for every female athlete on each 
+apparatus they were reported to have competed on. From these calculations, I decided to cut out most athletes 
+by only inspecting athletes that ranked in the top ten by mean score alone for each apparatus. This was a 
+reasonable elimination of data as the score values among the top ten candidates varied enough, often by over a 
+full point, to justify that athletes that never ranked in the top ten for a particular apparatus are not 
+competitive enough to medal at the Olympics.
 
@@
 
+Based on the plot of the top ten male athletes on the floor exercise apparatus I selected the parameter of 
+the score standard deviation subtracted from the mean score in order to identify the best suited five 
+athletes. Based on the parameter, the five ``best'' male athletes on floor exercise are Juda, Mccool, Young, Moldauer, 
+and Hong.
+
+Based on the plot of the top ten male athletes on the vault apparatus I selected the parameter of 
+the score standard deviation subtracted from the mean score in order to identify the best suited five 
+athletes. Based on the parameter, the five ``best'' male athletes on vault are Hale, Young, Malone, Briones, and 
+Juda.
+
+Based on the plot of the top ten male athletes on the still rings apparatus I selected the parameter of 
+half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
+athletes. Based on the parameter, the five ``best'' male athletes on still rings are Whittenburg, Briones, Diab, 
+Hong, and Loos.
+
+Based on the plot of the top ten male athletes on the pommel horse apparatus I selected the parameter of 
+half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
+athletes. Based on the parameter, the five ``best'' male athletes on pommel horse are Nedoroscik, Young, Malone, 
+Dang, and Bock.
+
+Based on the plot of the top ten male athletes on the parallel bars apparatus I selected the parameter of 
+half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
+athletes. Based on the parameter, the five ``best'' male athletes on parallel bars are Hong, Chou, Walker, Malone, 
+and Phillips.
+
+Based on the plot of the top ten male athletes on the high bar apparatus I selected the parameter of 
+half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
+athletes. Based on the parameter, the five ``best'' male athletes on high bar are Malone, Juda, Briones, Bold, and 
+Nguyen.
+
+Ultimately, the list of athletes that ranked among the top five United States male athletes 19 distinct 
+names. However, nine of these athletes have not competed on all six apparatuses, so they will not be considered 
+with the other ten athletes for individual or team all-around. Thus, the list of selected athletes that 
+are involved in future computations includes Juda, Young, Moldauer, Hong, Hale, Malone, Whittenburg, Loos, 
+Bock, and Walker.
+
 \bibliographystyle{chicago}

### 2024-01-10 manuscript/submission.tex
revising the appendix to only include essential content on the mens component

@@
   and High Bar Apparatus}
-  \label{fig:FA}
+  \label{fig:MA}
 \end{figure}
@@
   \caption{The best candidates for the male individual all-around and team all around medals}
-  \label{fig:FAA}
+  \label{fig:MAA}
 \end{figure}
@@
 
-When determining the most ideal American male candidates, 
-I did inspect the data of non United States gymnasts in order to determine which medals the United States 
-male team has the greatest chance of earning.
+\\
 
 Similar to the female model, I used the same method to determine the ``best'' male all-around candidates as I did for females. From 
-Figure~\ref{fig:IAAM} I determined that Juda and Malone are the best male Individual all-around candidates. From 
-Figure~\ref{fig:MAA3} I determined that Juda, Malone, and Young are the best male team all-around finalists 
-candidates. Additionally, from Figure~\ref{fig:MAA4} I determined that Moldauer is the best candidate to also compete 
+Figure~\ref{fig:MAA} I determined that Juda and Malone are the best male Individual all-around candidates, 
+Juda, Malone, and Young are the best male team all-around finalists, and Moldauer is the best candidate to also compete 
 with Juda, Malone, and Young in the all-around qualifying round. Comparatively, determining the ``best'' fifth Olympic 
@@
 we can see that many of our ``best'' candidates are still ranked very poorly globally, and therefore would not have a 
-strong liklihood of medalling at the olympics. Among all of the male USA athletes that are not yet selected, the only 
+strong liklihood of medalling at the Olympics. Among all of the male USA athletes that are not yet selected, the only 
 athlete that has a relatively decent chance of medaling is Hale, who ranks 6th globally for the Vault apparatus.
 
-Ultimately, in order to maximize the the number of medals the Unites States male team wins, I would comprise the 
-team of the athletes Juda, Malone, Young, Moldauer, and Hale.
-
-Based on the plot of the top ten male athletes on the floor exercise apparatus I selected the parameter of 
-the score standard deviation subtracted from the mean score in order to identify the best suited five 
-athletes. Based on the parameter, the five ``best'' male athletes on floor exercise are Juda, Mccool, Young, Moldauer, 
-and Hong.
-
-Based on the plot of the top ten male athletes on the vault apparatus I selected the parameter of 
-the score standard deviation subtracted from the mean score in order to identify the best suited five 
-athletes. Based on the parameter, the five ``best'' male athletes on vault are Hale, Young, Malone, Briones, and 
-Juda.
-
-Based on the plot of the top ten male athletes on the still rings apparatus I selected the parameter of 
-half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-athletes. Based on the parameter, the five ``best'' male athletes on still rings are Whittenburg, Briones, Diab, 
-Hong, and Loos.
-
-Based on the plot of the top ten male athletes on the pommel horse apparatus I selected the parameter of 
-half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-athletes. Based on the parameter, the five ``best'' male athletes on pommel horse are Nedoroscik, Young, Malone, 
-Dang, and Bock.
-
-Based on the plot of the top ten male athletes on the parallel bars apparatus I selected the parameter of 
-half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-athletes. Based on the parameter, the five ``best'' male athletes on parallel bars are Hong, Chou, Walker, Malone, 
-and Phillips.
-
-Based on the plot of the top ten male athletes on the high bar apparatus I selected the parameter of 
-half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
-athletes. Based on the parameter, the five ``best'' male athletes on high bar are Malone, Juda, Briones, Bold, and 
-Nguyen.
-
-Ultimately, the list of athletes that ranked among the top five United States male athletes 19 distinct 
-names. However, nine of these athletes have not competed on all six apparatuses, so they will not be considered 
-with the other ten athletes for individual or team all-around. Thus, the list of selected athletes that 
-are involved in future computations includes Juda, Young, Moldauer, Hong, Hale, Malone, Whittenburg, Loos, 
-Bock, and Walker.
+Ultimately, in order to maximize the the number of medals the Unites States male team wins, the team should be comprised  
+of the athletes Juda, Malone, Young, Moldauer, and Hale.
 

### 2024-01-10 manuscript/submission.tex
adding additional sources of error in the discussion section

@@
 
-In my preliminary steps, I calculated the mean and standard deviation for every female athlete on each 
-apparatus they were reported to have competed on. From these calculations, I decided to cut out most athletes 
-by only inspecting athletes that ranked in the top ten by mean score alone for each apparatus. This was a 
+Using an anatlytical method dependent on mean and standard deviation derived parameters, this paper 
+outlines a procedure for identifying the Team USA Olympic Women’s Artistic Gymnastics team that will optimize 
+success at the Olympics through numberically evaluating each USA athlete based on both their accuracy and precision. 
+Ultimately, Simone Biles, Shilese Jones, Konnor McClain, Kaliya Lincoln, and Jade Carey can be identified as the 
+the group of five athletes who will enable the Team USA Olympic Women’s Artistic Gymnastics teams to optimize 
+success at the 2024 Paris Summer Olympics based on this method.
+
+At various steps throughout the procedure large qualtities of athletes were eliminated from consideration 
+based on various analytical decisions. For example, most athletes were eliminated from consideration as 
+only athletes that ranked in the top ten by mean score alone for each apparatus were inspected. This was a 
 reasonable elimination of data as the score values among the top ten candidates varied enough, often by over a 
 full point, to justify that athletes that never ranked in the top ten for a particular apparatus are not 
-competitive enough to medal at the Olympics.
+competitive enough to medal at the Olympics. Furthermore, this list of athletes was also reduced by half by the 
+use of a subjectively determined paraemter, but this decision is also justified as only two athletes from each 
+country can compete for an apparatus medal, so reducing the considered candidates to only the top five for each 
+apparatus is reasonable as it would be highly unlikely for the 6th best USA candidate for a particualar apparatus 
+to medal at the Olympics.
+
+Notably, this algorithm is not powerful for strong athletes with few attempts on a particualr apparatus as individuals 
+with only one attempt could not possess a parameter value and thus were eliminated. Additionally, this algorithm 
+would not be strong for a country that is inferior at certain events as this model assumes athletes from the country 
+of interest have a reasonable chance at medaling in any category. As such, this model is designed to have the strongest 
+candidates competing in every category regardless of global rank in each category.
+
+Furthermore, the design of this method does not take into account the impact of difficulty or execution scores on 
+overall score. While this data could have been beneficially in selecting the most competitive or successful athletes 
+to comprise the Olympic team, existing literature doubted whether difficulty and execution scores should be 
+used as predictors at all.
+
+Ultimately, while this analytical method may not take into account all of the information and that that was available, 
+the method was able to identify a competitive group of athletes that represent the ``best'' athletes suited 
+to medal and optimize success in each of the Olympic events.
 

### 2024-01-15 manuscript/submission.tex
cleaned bib and fixed compiling errors
changing title for appropriateness

@@
 
-\title{Predicting The Success of The Female United States Artistic Gymnastics Team at The 2024 Paris Olympics 
-Using Mean and Standard Deviation Derived Parameters}
+\title{Selecting Team Members of The Female United States Artistic Gymnastics Team at The 2024 Paris Olympics 
+Based on Performance and Stability To Maximize Success}
 \author{Kathleen Houlihan\\
@@
 
+\citet{JonasRohleder2023} did something...
+
 At the Summer Olympics in Paris in 2024, ninety-six men and ninety-six women from around the world will 
@@
 category while also placing greatest importance on the team all-around medal.
-
-\\
 
@@
 
-\\
-
 As existing literature fails to suggest how data from major domestic and international gymnastics competitions 
@@
 candidates to compete on behalf of the United States at the Olympics.
-
-\\
 
@@
 of the Olympic outcomes in 2024 will be the most recent data.
-
-\\
 
@@
 
-\\
-
 Similar to the female model, I used the same method to determine the ``best'' male all-around candidates as I did for females. From 

### 2024-01-15 code/codeprocessfemale.Rmd
editing female code to have more visually appealing plots

@@
 library(cowplot)
+library(ggrepel)
 ```
@@
 
-#Create a table with the top 10 athletes with the highest mean scores for each apparatus and to plot each apparatus on separate graphs
+#Create a table with the top 10 athletes with the highest mean scores for each apparatus to plot each apparatus on separate graphs
   # Filter for USA female gymnasts
@@
   # Plot each apparatus on one graph
-  for (apparatus in unique(top_10_athletes$Apparatus)) {
-  data_subset <- filter(top_10_athletes, Apparatus == apparatus)
   p <- ggplot(top_10_athletes, aes(x = SD_Score, y = Mean_Score, label = LastName)) +
   geom_point() +
-  geom_text(hjust = 0, vjust = 0) +
+  geom_text_repel(box.padding = 0.25, point.padding = 0.25) +  
   labs(title = "Top 10 Female Athletes",
@@
   facet_wrap(~Apparatus, scales = "free") +
-  theme_minimal()
-  }
+  theme_minimal() +
+  theme(
+    panel.background = element_rect(fill = "gray85"),  
+    panel.grid.major = element_line(color = "white"),
+    axis.text = element_text(color = "black"),  
+    axis.title = element_text(color = "black"), 
+    plot.title = element_text(color = "black")  
+  )
 
@@
   geom_point() +
-  geom_text(hjust = 0, vjust = 0) +
-  labs(x = "Sum of Standard Deviations", y = "Sum of Means", title = "Female All-Around Candidates")
+  geom_text_repel(box.padding = 0.25, point.padding = 0.25) +
+  labs(x = "Sum of Standard Deviations", y = "Sum of Means", title = "Female All-Around Candidates") +
+  facet_wrap(~., scales = "free") +  
+  theme_minimal() +
+  theme(
+    panel.background = element_rect(fill = "gray85"),  
+    panel.grid.major = element_line(color = "white"),
+    axis.text = element_text(color = "black"),  
+    axis.title = element_text(color = "black"), 
+    plot.title = element_text(color = "black")  
+  )
 
@@
     geom_point() +
-  geom_text(aes(label = Combination), hjust = 0, vjust = 0) +
+    geom_text_repel(aes(label = Combination), box.padding = 0.25, point.padding = 0.25) +
     labs(x = "Sum of Standard Deviations", y = "Mean Score") +
-  ggtitle("Combinations of 3 Female Athletes")
+    ggtitle("Combinations of 3 Female Athletes") +
+    facet_wrap(~., scales = "free") +  
+    theme_minimal() +
+    theme(
+        panel.background = element_rect(fill = "gray85"),  
+        panel.grid.major = element_line(color = "white"),
+        axis.text = element_text(color = "black"),  
+        axis.title = element_text(color = "black"), 
+        plot.title = element_text(color = "black")  
+    )
 
@@
     geom_point() +
-  geom_text(aes(label = Combination), hjust = 0, vjust = 0) +
+    geom_text_repel(aes(label = Combination), box.padding = 0.25, point.padding = 0.25) +
     labs(x = "Sum of Standard Deviations", y = "Mean Score") +
-  ggtitle("Combinations of 4 Female Athletes")
+    ggtitle("Combinations of 4 Female Athletes") +
+    facet_wrap(~., scales = "free") +  
+    theme_minimal() +
+    theme(
+        panel.background = element_rect(fill = "gray85"),  
+        panel.grid.major = element_line(color = "white"),
+        axis.text = element_text(color = "black"),  
+        axis.title = element_text(color = "black"), 
+        plot.title = element_text(color = "black")  
+    )
 

### 2024-01-15 code/codeprocessmale.Rmd
updating male code to reflect better plot formatting

@@
   # Filter for USA male gymnasts
-  usa_female_scores <- data %>%
+  usa_male_scores <- data %>%
   filter(Country == "USA" & Gender == "m")
@@
   # Plot each apparatus on one graph
-  for (apparatus in unique(top_10_athletes$Apparatus)) {
-  data_subset <- filter(top_10_athletes, Apparatus == apparatus)
   p <- ggplot(top_10_athletes, aes(x = SD_Score, y = Mean_Score, label = LastName)) +
   geom_point() +
-  geom_text(hjust = 0, vjust = 0) +
-  labs(x = "Standard Deviation", y = "Mean Score") +
+  geom_text_repel(box.padding = 0.25, point.padding = 0.25) +  
+  labs(title = "Top 10 Male Athletes",
+       x = "Standard Deviation", y = "Mean Score") +
   facet_wrap(~Apparatus, scales = "free") +
-  theme_minimal()
+  theme_minimal() +
+  theme(
+    panel.background = element_rect(fill = "gray85"),  
+    panel.grid.major = element_line(color = "white"),
+    axis.text = element_text(color = "black"),  
+    axis.title = element_text(color = "black"), 
+    plot.title = element_text(color = "black")  
+  )
+
+   # Print the combined plot
   print(p)
-  }
 
@@
   geom_point() +
-  geom_text(hjust = 0, vjust = 0) +
-  labs(x = "Sum of Standard Deviations", y = "Sum of Means", title = "Male All-Around Candidates")
+  geom_text_repel(box.padding = 0.25, point.padding = 0.25) +
+  labs(x = "Sum of Standard Deviations", y = "Sum of Means", title = "Male All-Around Candidates") +
+  facet_wrap(~., scales = "free") +  
+  theme_minimal() +
+  theme(
+    panel.background = element_rect(fill = "gray85"),  
+    panel.grid.major = element_line(color = "white"),
+    axis.text = element_text(color = "black"),  
+    axis.title = element_text(color = "black"), 
+    plot.title = element_text(color = "black")  
+  )
 
@@
     geom_point() +
-  geom_text(aes(label = Combination), hjust = 0, vjust = 0) +
+    geom_text_repel(aes(label = Combination), box.padding = 0.25, point.padding = 0.25) +
     labs(x = "Sum of Standard Deviations", y = "Mean Score") +
-  ggtitle("Top 10 Combinations of 3 Male Athletes with Highest Mean Score")
+    ggtitle("Combinations of 3 Male Athletes") +
+    facet_wrap(~., scales = "free") +  
+    theme_minimal() +
+    theme(
+        panel.background = element_rect(fill = "gray85"),  
+        panel.grid.major = element_line(color = "white"),
+        axis.text = element_text(color = "black"),  
+        axis.title = element_text(color = "black"), 
+        plot.title = element_text(color = "black")  
+    )
 
@@
     geom_point() +
-  geom_text(aes(label = Combination), hjust = 0, vjust = 0) +
+    geom_text_repel(aes(label = Combination), box.padding = 0.25, point.padding = 0.25) +
     labs(x = "Sum of Standard Deviations", y = "Mean Score") +
-  ggtitle("Top 10 Combinations of 4 Male Athletes with Highest Mean Score")
+    ggtitle("Combinations of 4 Male Athletes") +
+    facet_wrap(~., scales = "free") +  
+    theme_minimal() +
+    theme(
+        panel.background = element_rect(fill = "gray85"),  
+        panel.grid.major = element_line(color = "white"),
+        axis.text = element_text(color = "black"),  
+        axis.title = element_text(color = "black"), 
+        plot.title = element_text(color = "black")  
+    )
 

### 2024-01-15 manuscript/submission.tex
making necessary formatting and figure changes

@@
 
-  Following the 2020 Toyko Olympics where the United States was the only country to have a team medal 
-  in all six of the women's artistic gymnastic events, the performance of the United States women's artistic 
-  gymnastics team at the 2024 Paris Summer Olympics is once again predicted to be the most watched Olympic 
-  dicipline both in the United States and globally. With the whole world anticipating the success of the United 
-  States women's team, it is crucial that the team of five women that are selected to represent the United States 
+  With the whole world anticipating the success of the United States women's artistic gymnastics team, 
+  it is crucial that the team of five women that are selected to represent the United States 
   are the athletes best suited to optimize success and maximize the expected medal count in Paris 2024. As there 
   are no preexisting statistical papers that methodize the selection of athletes for Olympic Gymnastic teams, 
-  this paper aims to answer the question of what metric should be used to judge the olympic canidacy of USA 
+  this paper aims to answer the question of what metric should be used to judge the Olympic canidacy of USA 
   gymnasts and to outline a statistical method that can be used presently and in the future to select the ``best'' 
@@
   the group of five athletes who will enable the Team USA Olympic Women’s Artistic Gymnastics team to optimize 
-  success through numberically evaluating each USA athlete based on both their accuracy and precision in order to 
+  success through numberically evaluating each USA athlete based on both their performance and stability in order to 
   more accurately identify the ``best'' team candidates. Through application of this analytical method to present 
@@
 
-\citet{JonasRohleder2023} did something...
+Following the 2020 Toyko Olympics where the United States was the only country to have a team medal 
+in all six of the women's artistic gymnastic events, the performance of the United States women's artistic 
+gymnastics team at the 2024 Paris Summer Olympics is once again predicted to be the most watched Olympic 
+dicipline both in the United States and globally. With the whole world anticipating the success of the United 
+States women's team, it is crucial that the team of five women that are selected to represent the United States 
+are the athletes best suited to optimize success and maximize the expected medal count in Paris 2024.
 
@@
 Paris Summer Olympics or at recent olympics. However, there is literature that relates to various aspects of 
-the data that will be used to form my predictions. For example, the article ``The Prediction of All-Around 
-Event Final Score Based On D and E Score Factors In Women's Artistic Gymnastics'' aims to determine the 
+the data that will be used to form my predictions. For example, the article \citet{ScienceOfGymnastics2021} aims to determine the 
 impact of individual apparatus difficulty and execution scores on overall score. 
 Expertise from this article could be useful in allowing us to understand how difficulty and execution scores 
-play a role in predicting the overall score. Additionally, the paper 
-``Performance rating in men’s world elite artistic gymnastics: a status-quo study on scoring 
-tendencies at Olympic Games following rule changes'' also can play a similar role in predicting overall 
+play a role in predicting the overall score. Additionally, the article \citet{JonasRohleder2023} 
+also can play a similar role in predicting overall 
 score. Notably, the paper found that recent Olympic rule changes resulted in significantly enhanced performance 
 differentiation with the execution score being the main predictor of the final score. 
-Furthermore, in the article ``How Apparatus Difficulty Scores Affect All 
-Around Results in Men's Artistic Gymnastics,'' the authors use regression, cluster, and ANOVA analysis to 
+Furthermore, in the article \citet{ApparatusDifficulty2010} the authors use regression, cluster, and ANOVA analysis to 
 analyze how difficulty scores predict overall score differently across different apparatuses. However, in this 
@@
 \begin{enumerate}
+  \item Determine the best individual apparatus candidates.
+  \begin{enumerate}
     \item Calculate and examine the mean and standard deviations of each American female athlete's score 
@@
     \end{enumerate}
+  \end{enumerate}
+  \item Determine the best individual all-around candidates.
+  \begin enumerate
    \item Produce a list of ``target athletes'' for furture computations that contains all athletes that were identified 
@@
    \end{enumerate}
+  \end{enumerate}
+  \item Determine the best team all-around candidates.
+  \begin{enumerate}
    \item Calculate the summed mean score and standard deviation sum of every combination of three athletes using the previously 
@@
    \end{enumerate}
+  \end{enumerate}
 \item Visully exammine each produced plot to build a final team of five in an effort to include in 
@@
     the best two candidates for the individual all-around, and the two athletes that are superior on each apparatus.
-
 \end{enumerate}
@@
   \centering
-  \includegraphics[scale=0.7]{FemaleAthleteApparatus.pdf}
-  \caption{Top 10 Female Candidates for the Olympic Balance Beam, Floor Exercise, Uneven Bars, and Vault Apparatus}
+  \includegraphics[scale=0.7]{FinalFemaleApparatusPlot.pdf}
+  \caption{Top 10 Female Candidates for the Olympic Balance Beam, Floor Exercise, Uneven Bars, and Vault Apparatus.}
   \label{fig:FA}
@@
   \caption{Top ten female candidates for each apparatus based on mean score alone and 
-  their $\mu - \alpha \sigma$ parameter values}
+  their $\mu - \alpha \sigma$ parameter values.}
   \label{tab:tableBBP}
@@
   \centering
-  \includegraphics[scale=0.55]{FemaleMultipleAllAround.pdf}
-  \caption{The best candidates for the female individual all-around and team all around medals}
+  \includegraphics[scale=0.55]{FinalFemaleAllAroundPlot.pdf}
+  \caption{The best candidates for the female individual all-around and team all around medals.}
   \label{fig:FAA}
@@
 
-\section{Appendix: Application of the Mean and Standard Deviation Derived Parameters Methods For The Male 
-United States Artistic Gymnastics Team at The 2024 Paris Olympics}
+\section{Application of Methods To The Male USA Artistic Gymnastics Team}
 
@@
   \centering
-  \includegraphics[scale=0.5]{MaleAthleteApparatus.pdf}
+  \includegraphics[scale=0.5]{FinalMaleApparatusPlot.pdf}
   \caption{Top 10 Male Candidates for the Olympic Floor Exercise, Pommel Horse, Still Rings, Vault, Parallel Bars, 
-  and High Bar Apparatus}
+  and High Bar Apparatus.}
   \label{fig:MA}
@@
   \centering
-  \includegraphics[scale=0.7]{MaleMultipleAllAround.pdf}
-  \caption{The best candidates for the male individual all-around and team all around medals}
+  \includegraphics[scale=0.7]{FinalMaleAllAroundPlot.pdf}
+  \caption{The best candidates for the male individual all-around and team all around medals.}
   \label{fig:MAA}

### 2024-01-15 manuscript/submission.tex
reorganizing numbered method list

@@
     \begin{enumerate}
-      \item Use these plots as a visual to represent the possible scores that could be achielved in each apparatus 
+      \item Use these plots as a visual to represent the possible scores that could be achieved in each apparatus 
      component of the Olympics.
@@
      \end{enumerate}
-     \item Identify the athletes with the two largest paramter values as the ``best'' on each apparatus.
+     \item Identify the athletes with the two largest parameter values as the ``best'' on each apparatus.
     \end{enumerate}
@@
   \item Determine the best individual all-around candidates.
-  \begin enumerate
-   \item Produce a list of ``target athletes'' for furture computations that contains all athletes that were identified 
+  \begin{enumerate}
+   \item Produce a list of ``target athletes'' for future computations that contains all athletes that were identified 
    as being in the top five for any apparatus in the last step.
    \begin{enumerate}
-     \item Remove any athletes from the ``target athletes'' list that have not competed on all aparatuses.
+     \item Remove any athletes from the ``target athletes'' list that have not competed on all apparatuses.
    \end{enumerate}
@@
    \begin{enumerate}
-     \item Use this plot as a visual to represent the possible scores that could be achielved in the individual all-around 
+     \item Use this plot as a visual to represent the possible scores that could be achieved in the individual all-around 
      component of the Olympics.
@@
   \end{enumerate}
+
 \item Determine the best team all-around candidates.
@@
    \begin{enumerate}
-     \item Use this plot as a visual to represent the possible scores that could be achielved in the all-around team finals 
+     \item Use this plot as a visual to represent the possible scores that could be achieved in the all-around team finals 
     component of the Olympics.
@@
    \begin{enumerate}
-      \item Use this plot as a visual to represent the possible scores that could be achielved in the all-around team qualifying  
+      \item Use this plot as a visual to represent the possible scores that could be achieved in the all-around team qualifying  
      round of the Olympics.
@@
   \end{enumerate}
-\item Visully exammine each produced plot to build a final team of five in an effort to include in 
+
+\item Visually examine each produced plot to build a final team of five in an effort to include in 
     the final team the best three candidates for the team all-around, the best candidate for the fourth qualifying position, 

### 2024-01-16 manuscript/submission.tex
fixing citation references and correcting spelling errors

@@
   are no preexisting statistical papers that methodize the selection of athletes for Olympic Gymnastic teams, 
-  this paper aims to answer the question of what metric should be used to judge the Olympic canidacy of USA 
+  this paper aims to answer the question of what metric should be used to judge the Olympic candidacy of USA 
   gymnasts and to outline a statistical method that can be used presently and in the future to select the ``best'' 
-  gymnasts to comprise the United States women's Olympic team in order to maximize success. Using an anatlytical 
+  gymnasts to comprise the United States women's Olympic team in order to maximize success. Using an analytical 
   method dependent on mean and standard deviation derived parameters, this paper outlines a procedure for identifying 
   the group of five athletes who will enable the Team USA Olympic Women’s Artistic Gymnastics team to optimize 
-  success through numberically evaluating each USA athlete based on both their performance and stability in order to 
+  success through numerically evaluating each USA athlete based on both their performance and stability in order to 
   more accurately identify the ``best'' team candidates. Through application of this analytical method to present 
@@
 gymnastics team at the 2024 Paris Summer Olympics is once again predicted to be the most watched Olympic 
-dicipline both in the United States and globally. With the whole world anticipating the success of the United 
+discipline both in the United States and globally. With the whole world anticipating the success of the United 
 States women's team, it is crucial that the team of five women that are selected to represent the United States 
@@
 At the Summer Olympics in Paris in 2024, ninety-six men and ninety-six women from around the world will 
-represent their countries and compete in the artistic gymnatics dicipline. The overall importance of the Olympics 
+represent their countries and compete in the artistic gymnastics discipline. The overall importance of the Olympics 
 cannot be understated as the games are a symbol of peaceful global interaction and give people hope that a better 
@@
 (see Appendix). Noting that Olympic ``success'' can be interpreted in a number of ways, the methods of this 
-paper are designed to maximize the overall medal count by maximizing the USA team's opportrunities to medal in each 
+paper are designed to maximize the overall medal count by maximizing the USA team's opportunities to medal in each 
 category while also placing greatest importance on the team all-around medal.
@@
 Paris Summer Olympics or at recent olympics. However, there is literature that relates to various aspects of 
-the data that will be used to form my predictions. For example, the article \citet{ScienceOfGymnastics2021} aims to determine the 
+the data that will be used to form my predictions. For example, the article by \citet{ScienceOfGymnastics2021} aims to determine the 
 impact of individual apparatus difficulty and execution scores on overall score. 
 Expertise from this article could be useful in allowing us to understand how difficulty and execution scores 
-play a role in predicting the overall score. Additionally, the article \citet{JonasRohleder2023} 
-also can play a similar role in predicting overall 
+play a role in predicting the overall score. Additionally, the article by \citet{JonasRohleder2023} 
+can also play a similar role in predicting overall 
 score. Notably, the paper found that recent Olympic rule changes resulted in significantly enhanced performance 
 differentiation with the execution score being the main predictor of the final score. 
-Furthermore, in the article \citet{ApparatusDifficulty2010} the authors use regression, cluster, and ANOVA analysis to 
+Furthermore, in the article by \citet{ApparatusDifficulty2010}, the authors use regression, cluster, and ANOVA analysis to 
 analyze how difficulty scores predict overall score differently across different apparatuses. However, in this 
-article the authors found that while difficulty scores may have predictive tendancies for some apparatuses, 
+article the authors found that while difficulty scores may have predictive tendencies for some apparatuses, 
 the strength of the prediction varied drastically from apparatus to apparatus, with there being little to no 
@@
 the analytical method presented in this paper aims to outline a procedure that takes into account data from recent 
-gymnastics competitions and Olympic competition structure in orer to identify the group of five athletes who will 
+gymnastics competitions and Olympic competition structure in order to identify the group of five athletes who will 
 enable the Team USA Olympic Women’s Artistic Gymnastics team to optimize success in Paris 2024. If Olympic 
 competition structure and recent competitive scores on each apparatus are taken into consideration, then an 
-anatlytical method dependent on mean and standard deviation derived parameters can be used to identify the foremost 
+analytical method dependent on mean and standard deviation derived parameters can be used to identify the foremost 
 candidates to compete on behalf of the United States at the Olympics.
@@
 this project in Section~\ref{sec:data}. Then, I will discuss my 
-analytical methods to determine the atheltes that should be sent to the Olympics from the United States 
+analytical methods to determine the athletes that should be sent to the Olympics from the United States 
 in Section~\ref{sec:meth}. Later, I will present the results of my 
@@
 
-For the purposes of this research design, when determining the most ideal feamle olympic candidates, 
+For the purposes of this research design, when determining the most ideal female olympic candidates, 
 only data on female United States gymnasts is analyzed, presuming that the United States 
@@
 two attempts on the vault apparatus. In an effort to interpret the data as accurately as possible and avoid having 
-multiple statistics for one athlete on the same apparatus, this discrepency is corrected by merging ``VT,'' ``VT1,'' and 
+multiple statistics for one athlete on the same apparatus, this discrepancy is corrected by merging ``VT,'' ``VT1,'' and 
 ``VT2'' to all be reported as ``VT.'' Also, the data source is flawed as it alternates between reporting athlete names
@@
 In order to reduce the vast list of United States female gymnasts to just five athletes, the proposed method in 
-this paper utilizes a paramter value of the score standard deviation multipled by some alpha value subtracted 
-from the mean score for each apparatus, or $\mu - \alpha \sigma$. This paramter value serves to rank athletes based 
-on having both a high mean score for a particualr event and low standard deviation. By subtracting the standard deviation 
+this paper utilizes a parameter value of the score standard deviation multiplied by some alpha value subtracted 
+from the mean score for each apparatus, or $\mu - \alpha \sigma$. This parameter value serves to rank athletes based 
+on having both a high mean score for a particular event and low standard deviation. By subtracting the standard deviation 
 from the mean score, we are able to identify the ``best'' athletes as having the highest parameter values. 
@@
 However, in cases where the rank produced by the parameter value selects athletes with comparatively low mean scores and 
-low standrad deviations prior to athletes with significantly higher mean scores and slightly high standard deviations, 
+low standard deviations prior to athletes with significantly higher mean scores and slightly high standard deviations, 
 this alpha value should be reduced until the rank of the athletes coordinates with the order that seems visually most 
@@
 athletes for each apparatus and typically play the largest role in determining which athletes are included at the margin. 
-Ultimately, if an athlete is bordering being 4th, 5th, 6th, or 7th best for a particualr apparatus in the United States 
+Ultimately, if an athlete is bordering being 4th, 5th, 6th, or 7th best for a particular apparatus in the United States 
 and the athlete is not superior on another apparatus, it is highly unlikely that they would be selected for the Olympic 
-team at all. In cases where an athlete only has one observation for a prticular apparatus, the 
+team at all. In cases where an athlete only has one observation for a particular apparatus, the 
 standard deviation value is unavailable and thus the parameter value cannot be calculated. For the purposes of this 
@@
 \midrule
-biles & 14.38 & biles & 14.55 & jones & 14.26 & Biles & 14.78\\
+biles & 14.38 & biles & 14.55 & jones & 14.26 & biles & 14.78\\
 \midrule
-mcclain & 14.14 & lincoln & 13.73 & biles & 14.17 & Carey & 14.36\\
+mcclain & 14.14 & lincoln & 13.73 & biles & 14.17 & carey & 14.36\\
 \midrule
-lee & 13.69 & carey & 13.41 & wong & 13.59 & Mcclain & 14.20\\
+lee & 13.69 & carey & 13.41 & wong & 13.59 & mcclain & 14.20\\
 \midrule
-sumanasekera & 12.95 & dicello & 13.4 & matthews & 13.50 & Jones & 14.20\\
+sumanasekera & 12.95 & dicello & 13.4 & matthews & 13.50 & jones & 14.20\\
 \midrule
-blakely & 12.78 & chiles & 13.38 & blakely & 13.49 & Chiles & 14.11\\
+blakely & 12.78 & chiles & 13.38 & blakely & 13.49 & chiles & 14.11\\
 \midrule
@@
 the score standard deviation subtracted from the mean score in order to identify the best suited five 
-athletes. Based on the parameter displayed in table~\ref[tablebbp], the five ``best'' female athletes on balance beam are Biles, Mcclain, 
-Lee, Sumanasekera, and Blakely with Biles and McClain being expert for this apparatus. Simialrly, the five ``best'' 
+athletes. Based on the parameter displayed in table~\ref[tablebbp], the five ``best'' female athletes on balance beam are Biles, McClain, 
+Lee, Sumanasekera, and Blakely with Biles and McClain being expert for this apparatus. Similarly, the five ``best'' 
 female athletes for floor exercise are Biles, Lincoln, Carey, 
@@
 Ultimately, the list of athletes that ranked among the top five United States female athletes includes Biles, 
-Mcclain, Lee, Sumanasekera, Blakely, Carey, Jones, Chiles, Wong, Matthews, Lincoln, and Dicello. However, Lee 
+McClain, Lee, Sumanasekera, Blakely, Carey, Jones, Chiles, Wong, Matthews, Lincoln, and Dicello. However, Lee 
 only has reported data for two out of four of the female apparatuses so she will not be considered with the other 
@@
 Based on the plots in figure~\ref{fig:FAA}, it is very clear that Biles is strong candidate to 
-compete for the individual all-around medal. However, it is not clear whether Jones or Mcclain is better suited 
+compete for the individual all-around medal. However, it is not clear whether Jones or McClain is better suited 
 to be the second United States individual all-around candidate. Looking at the data values and plot of the combinations of three athletes, 
-it is clear that Biles, Jones, and Mcclain are by far the best suited trio to compete for the team all-around medal. 
-Additionally, since this data suggests that both Mcclain and Jones should compete in the qualifying round, there 
+it is clear that Biles, Jones, and McClain are by far the best suited trio to compete for the team all-around medal. 
+Additionally, since this data suggests that both McClain and Jones should compete in the qualifying round, there 
 is no need to select one over the other for the second individual all-around candidate spot as they would both get 
@@
 team of the best two United States athletes for each apparatus. Based on the computations and plots, the superior two 
-athletes on balance beam are Biles and Mcclain, the superior two athletes on floor exercise are Biles and Lincoln, 
+athletes on balance beam are Biles and McClain, the superior two athletes on floor exercise are Biles and Lincoln, 
 the superior two athletes on uneven bars are Jones and Biles, and the superior two athletes on vault are Biles 
@@
 Hence, based on the proposed method, in order to maximize the number of medals the Unites States female team wins, 
-the team should be comprised of the athletes Biles, Jones, Mcclain, Lincoln, and Carey.
+the team should be comprised of the athletes Biles, Jones, McClain, Lincoln, and Carey.
 
@@
 
-Using an anatlytical method dependent on mean and standard deviation derived parameters, this paper 
+Using an analytical method dependent on mean and standard deviation derived parameters, this paper 
 outlines a procedure for identifying the Team USA Olympic Women’s Artistic Gymnastics team that will optimize 
-success at the Olympics through numberically evaluating each USA athlete based on both their accuracy and precision. 
+success at the Olympics through numerically evaluating each USA athlete based on both their accuracy and precision. 
 Ultimately, Simone Biles, Shilese Jones, Konnor McClain, Kaliya Lincoln, and Jade Carey can be identified as the 
@@
 
-At various steps throughout the procedure large qualtities of athletes were eliminated from consideration 
+At various steps throughout the procedure large quantities of athletes were eliminated from consideration 
 based on various analytical decisions. For example, most athletes were eliminated from consideration as 
@@
 competitive enough to medal at the Olympics. Furthermore, this list of athletes was also reduced by half by the 
-use of a subjectively determined paraemter, but this decision is also justified as only two athletes from each 
+use of a subjectively determined parameter, but this decision is also justified as only two athletes from each 
 country can compete for an apparatus medal, so reducing the considered candidates to only the top five for each 
-apparatus is reasonable as it would be highly unlikely for the 6th best USA candidate for a particualar apparatus 
+apparatus is reasonable as it would be highly unlikely for the 6th best USA candidate for a particular apparatus 
 to medal at the Olympics.
 
-Notably, this algorithm is not powerful for strong athletes with few attempts on a particualr apparatus as individuals 
+Notably, this algorithm is not powerful for strong athletes with few attempts on a particular apparatus as individuals 
 with only one attempt could not possess a parameter value and thus were eliminated. Additionally, this algorithm 
@@
 we can see that many of our ``best'' candidates are still ranked very poorly globally, and therefore would not have a 
-strong liklihood of medalling at the Olympics. Among all of the male USA athletes that are not yet selected, the only 
+strong likelihood of medalling at the Olympics. Among all of the male USA athletes that are not yet selected, the only 
 athlete that has a relatively decent chance of medaling is Hale, who ranks 6th globally for the Vault apparatus.

### 2024-01-16 manuscript/submission.tex
removing table midlines

@@
 biles & 14.38 & biles & 14.55 & jones & 14.26 & biles & 14.78\\
-\midrule
+
 mcclain & 14.14 & lincoln & 13.73 & biles & 14.17 & carey & 14.36\\
-\midrule
+
 lee & 13.69 & carey & 13.41 & wong & 13.59 & mcclain & 14.20\\
-\midrule
+
 sumanasekera & 12.95 & dicello & 13.4 & matthews & 13.50 & jones & 14.20\\
-\midrule
+
 blakely & 12.78 & chiles & 13.38 & blakely & 13.49 & chiles & 14.11\\
-\midrule
+
 jones & 12.58 & jones & 13.29 & greaves & 13.47 & sumanasekera & 14.07\\
-\midrule
+
 roberson & 12.50 & mcclain & 13.21 & miller & 13.38 & blakely & 14.05\\
-\midrule
+
 wong & 12.48 & wong & 13.16 & chiles & 13.34 & dicello & 13.88\\
-\midrule
+
 dicello & 12.45 & roberson & 12.98 & zhou & 13.28 & richardson & NA\\
-\midrule
+
 frazier & NA & frazier & NA & walker & NA & torry & NA\\
@@
 
-Based on the plot of the top ten female athletes on the balance beam apparatus in figure~\ref{fig:FA} I selected the parameter of 
+Based on the plot of the top ten female athletes on the balance beam apparatus in Figure~\ref{fig:FA} I selected the parameter of 
 the score standard deviation subtracted from the mean score in order to identify the best suited five 
-athletes. Based on the parameter displayed in table~\ref[tablebbp], the five ``best'' female athletes on balance beam are Biles, McClain, 
+athletes. Based on the parameter displayed in Table~\ref[tableBBP], the five ``best'' female athletes on balance beam are Biles, McClain, 
 Lee, Sumanasekera, and Blakely with Biles and McClain being expert for this apparatus. Similarly, the five ``best'' 
@@
 
-Based on the plots in figure~\ref{fig:FAA}, it is very clear that Biles is strong candidate to 
+Based on the plots in Figure~\ref{fig:FAA}, it is very clear that Biles is strong candidate to 
 compete for the individual all-around medal. However, it is not clear whether Jones or McClain is better suited 

### 2024-01-16 manuscript/submission.tex
fixing table reference

@@
   their $\mu - \alpha \sigma$ parameter values.}
-  \label{tab:tableBBP}
+  \label{table:1}
 \centering
@@
 the score standard deviation subtracted from the mean score in order to identify the best suited five 
-athletes. Based on the parameter displayed in Table~\ref[tableBBP], the five ``best'' female athletes on balance beam are Biles, McClain, 
+athletes. Based on the parameter displayed in Table~\ref{table:1}, the five ``best'' female athletes on balance beam are Biles, McClain, 
 Lee, Sumanasekera, and Blakely with Biles and McClain being expert for this apparatus. Similarly, the five ``best'' 

### 2024-01-16 manuscript/submission.tex
trimming intro and data section to meet word count

@@
 
-Following the 2020 Toyko Olympics where the United States was the only country to have a team medal 
-in all six of the women's artistic gymnastic events, the performance of the United States women's artistic 
-gymnastics team at the 2024 Paris Summer Olympics is once again predicted to be the most watched Olympic 
-discipline both in the United States and globally. With the whole world anticipating the success of the United 
-States women's team, it is crucial that the team of five women that are selected to represent the United States 
-are the athletes best suited to optimize success and maximize the expected medal count in Paris 2024.
-
-At the Summer Olympics in Paris in 2024, ninety-six men and ninety-six women from around the world will 
-represent their countries and compete in the artistic gymnastics discipline. The overall importance of the Olympics 
-cannot be understated as the games are a symbol of peaceful global interaction and give people hope that a better 
-world is possible. For decades, gymnastics has been the most watched sport in the Summer Olympics and the United 
+For decades, gymnastics has been the most watched sport in the Summer Olympics and the United 
 States has been known for bringing gold medal-winning gymnasts to compete. In the 2020 
@@
 the male team, the focus of this paper is aimed at identifying a method that best isolates strong female gymnasts 
-that would be prime candidates for the 2024 and future Olympics. Later in this paper, the designed statistical 
-method is applied to the male team, which is anticipated to earn fewer medals than the female team, if any 
-(see Appendix). Noting that Olympic ``success'' can be interpreted in a number of ways, the methods of this 
+that would be prime candidates for the 2024 and future Olympics. Noting that Olympic ``success'' can be interpreted in a number 
+of ways, the methods of this 
 paper are designed to maximize the overall medal count by maximizing the USA team's opportunities to medal in each 
@@
 impact of individual apparatus difficulty and execution scores on overall score. 
-Expertise from this article could be useful in allowing us to understand how difficulty and execution scores 
-play a role in predicting the overall score. Additionally, the article by \citet{JonasRohleder2023} 
+ Additionally, the article by \citet{JonasRohleder2023} 
 can also play a similar role in predicting overall 
-score. Notably, the paper found that recent Olympic rule changes resulted in significantly enhanced performance 
+score. Notably, this paper found that recent Olympic rule changes resulted in significantly enhanced performance 
 differentiation with the execution score being the main predictor of the final score. 
@@
 the strength of the prediction varied drastically from apparatus to apparatus, with there being little to no 
-predictive ability for some apparatuses. Ultimately, the available literature on predicting artistic 
-gymnastic scores seemed generally limited to how difficulty and execution scores predict overall score, 
-but some aspects of this literature casts doubt on whether difficulty and execution scores should be 
-used as predictors at all.
+predictive ability for some apparatuses. Ultimately, the available literature on predicting 
+gymnastic success seems generally limited to how difficulty and execution scores predict overall score.
 
@@
 gymnastics competitions and Olympic competition structure in order to identify the group of five athletes who will 
-enable the Team USA Olympic Women’s Artistic Gymnastics team to optimize success in Paris 2024. If Olympic 
-competition structure and recent competitive scores on each apparatus are taken into consideration, then an 
-analytical method dependent on mean and standard deviation derived parameters can be used to identify the foremost 
-candidates to compete on behalf of the United States at the Olympics.
+enable the Team USA Olympic Women’s Artistic Gymnastics team to optimize success in Paris 2024.
 
@@
 in Section~\ref{sec:meth}. Later, I will present the results of my 
-methods in Section~\ref{sec:res}. Lastly, I will discuss the meaning of my results, some challenges, 
-and some limitations of this project in Section~\ref{sec:dis}.
+methods in Section~\ref{sec:res}. Next, I will discuss the meaning of my results, some challenges, 
+and some limitations of this project in Section~\ref{sec:dis}. Finally, in  Appendix~\ref{appendix:men}, the designed statistical 
+method is applied to the male team, which is anticipated to earn fewer medals than the female team, if any.
 
@@
 
-For the purposes of this research design, when determining the most ideal female olympic candidates, 
+For the purposes of this research design, when determining the most ideal female Olympic candidates, 
 only data on female United States gymnasts is analyzed, presuming that the United States 
@@
 However, several data processing steps are required to correct several inconsistencies in the data source prior to 
-analytical computations being performed.
-First, the data is processed to remove any scores of zero based on the assumption that these may 
-be indicative of missing scores and that instances of these scores are rare. The decision to eliminate scores of 
-zero is further justified for the purposes of knowing the true mean scores of each athlete on each 
-apparatus for each successful attempt. Additionally, for some athletes and competitions vault
-scores are reported as ``VT,'' ``VT1,'' and ``VT2.'' This discrepancy is due to the fact that athletes are permitted
-two attempts on the vault apparatus. In an effort to interpret the data as accurately as possible and avoid having 
-multiple statistics for one athlete on the same apparatus, this discrepancy is corrected by merging ``VT,'' ``VT1,'' and 
-``VT2'' to all be reported as ``VT.'' Also, the data source is flawed as it alternates between reporting athlete names
-in upper or lower case letters. In order to correct this, all last names are converted to lower case for consistency 
-purposes. Lastly, the data source is inconsistent in the manner that it reports the first names of athletes as certain
-athletes are listed using only their first name at some competitions and are listed using their first and middle names 
-under the ``first name'' category for other competitions. In order to resolve this discrepancy, manual verification was used
-to ensure that any athletes listed under two names were the same person and that there were no United States  
-athletes with the same last name so that all statistical computations could be completed through grouping by last 
-name alone.
+analytical computations being performed:
+
+\begin{enumerate}
+\item Remove any scores of zero for the purposes of knowing the true mean scores of each athlete on each 
+apparatus for each successful attempt based on the assumption that these may 
+be indicative of missing scores and that instances of these scores are rare.
+\item Merge ``VT,'' ``VT1,'' and ``VT2'' to all be reported as ``VT'' to avoid having 
+multiple statistics for one athlete on the same apparatus.
+\item Convert all last names to lower case for consistency purposes.
+\end{enumerate}
 
@@
 \section{Application of Methods To The Male USA Artistic Gymnastics Team}
+\label{appendix:men}
 

### 2024-01-16 manuscript/submission.tex
trimming results section to meet word count

@@
 
-In order to reduce the vast list of United States female gymnasts to just five athletes, the proposed method in 
+In order to reduce the list of USA gymnasts to just five athletes, the proposed method in 
 this paper utilizes a parameter value of the score standard deviation multiplied by some alpha value subtracted 
 from the mean score for each apparatus, or $\mu - \alpha \sigma$. This parameter value serves to rank athletes based 
-on having both a high mean score for a particular event and low standard deviation. By subtracting the standard deviation 
-from the mean score, we are able to identify the ``best'' athletes as having the highest parameter values. 
+on having both a high mean score for a particular event and low standard deviation. 
 This alpha value is decided by examining the plots of the mean versus the standard deviation of the ten athletes 
@@
 and the athlete is not superior on another apparatus, it is highly unlikely that they would be selected for the Olympic 
-team at all. In cases where an athlete only has one observation for a particular apparatus, the 
-standard deviation value is unavailable and thus the parameter value cannot be calculated. For the purposes of this 
-research, it is reasonable to ignore any athletes who have only competed once on a particular apparatus as they would 
+team at all. For the purposes of this research, it is reasonable to ignore any athletes who have only competed once 
+on a particular apparatus and do not have a parameter value as they would 
 likely not be selected to compete on that apparatus at the Olympics.
@@
 
-Ultimately, the list of athletes that ranked among the top five United States female athletes includes Biles, 
-McClain, Lee, Sumanasekera, Blakely, Carey, Jones, Chiles, Wong, Matthews, Lincoln, and Dicello. However, Lee 
-only has reported data for two out of four of the female apparatuses so she will not be considered with the other 
-eleven athletes for individual or team all-around.
-
 \begin{figure}
@@
 Based on the plots in Figure~\ref{fig:FAA}, it is very clear that Biles is strong candidate to 
-compete for the individual all-around medal. However, it is not clear whether Jones or McClain is better suited 
-to be the second United States individual all-around candidate. Looking at the data values and plot of the combinations of three athletes, 
+compete for the individual all-around medal. Looking at the data values and plot of the combinations of three athletes, 
 it is clear that Biles, Jones, and McClain are by far the best suited trio to compete for the team all-around medal. 
-Additionally, since this data suggests that both McClain and Jones should compete in the qualifying round, there 
-is no need to select one over the other for the second individual all-around candidate spot as they would both get 
-the opportunity to qualify, and their scores at the Olympics will determine which athlete, if either, will qualify 
-to attend the individual all-around finals. Looking at plot of the combinations of four athletes, it is not clear whether Chiles, Carey, or 
+Looking at plot of the combinations of four athletes, it is not clear whether Chiles, Carey, or 
 Blakely is best suited to be the fourth team all-around candidate as their means and standard deviations are very 
-similar. However, looking at the individual apparatus events provides justification for who to ultimately select. 
-Knowing that two athletes per country can compete for an apparatus medal, it is strategic to try to compose the 
-team of the best two United States athletes for each apparatus. Based on the computations and plots, the superior two 
+similar. However, based on the computations and plots, the superior two 
 athletes on balance beam are Biles and McClain, the superior two athletes on floor exercise are Biles and Lincoln, 
@@
 since Carey is one of the candidates being considering for the all-around qualifying round and she is one of our superior 
-athletes on vault, it is reasonable to also select her to be the final member of the Olympic team. Although, the 
-summed combination that included Carey has the lowest mean in comparison to the combinations including Chiles or 
-Blakely, the selection of Carey can be further justified by the facts that the summed mean score difference is 
-within one point the combination including Carey has the lowest summed standard deviation.
+athletes on vault, it is reasonable to also select her to be the final member of the Olympic team.
 
@@
 USA gymnast that ranked globally in the top ten for a particular apparatus based on mean score alone. 
-
-Similar to the female model, I used the same method to determine the ``best'' male all-around candidates as I did for females. From 
-Figure~\ref{fig:MAA} I determined that Juda and Malone are the best male Individual all-around candidates, 
-Juda, Malone, and Young are the best male team all-around finalists, and Moldauer is the best candidate to also compete 
-with Juda, Malone, and Young in the all-around qualifying round. Comparatively, determining the ``best'' fifth Olympic 
-teammate is challenging as there are several apparatuses where our ``best'' competitor is not among the four 
-previously selected teammates. However, through examining the the mean score for every male gymnast on every apparatus 
-we can see that many of our ``best'' candidates are still ranked very poorly globally, and therefore would not have a 
-strong likelihood of medalling at the Olympics. Among all of the male USA athletes that are not yet selected, the only 
-athlete that has a relatively decent chance of medaling is Hale, who ranks 6th globally for the Vault apparatus.
-
 Ultimately, in order to maximize the the number of medals the Unites States male team wins, the team should be comprised  

### 2024-01-16 manuscript/submission.tex
trimming redundant info to hit word count

@@
   it is crucial that the team of five women that are selected to represent the United States 
-  are the athletes best suited to optimize success and maximize the expected medal count in Paris 2024. As there 
-  are no preexisting statistical papers that methodize the selection of athletes for Olympic Gymnastic teams, 
-  this paper aims to answer the question of what metric should be used to judge the Olympic candidacy of USA 
+  are the athletes best suited to optimize success and maximize the expected medal count in Paris 2024. 
+  This paper aims to answer the question of what metric should be used to judge the Olympic candidacy of USA 
   gymnasts and to outline a statistical method that can be used presently and in the future to select the ``best'' 
@@
 Currently there is no literature available relevant to predicting gymnastics outcomes at the 2024 
-Paris Summer Olympics or at recent olympics. However, there is literature that relates to various aspects of 
-the data that will be used to form my predictions. For example, the article by \citet{ScienceOfGymnastics2021} aims to determine the 
+Paris Summer Olympics or at recent olympics, but there is literature that relates to various aspects of 
+the data. For example, the article by \citet{ScienceOfGymnastics2021} aims to determine the 
 impact of individual apparatus difficulty and execution scores on overall score. 
  Additionally, the article by \citet{JonasRohleder2023} 
-can also play a similar role in predicting overall 
-score. Notably, this paper found that recent Olympic rule changes resulted in significantly enhanced performance 
+found that recent Olympic rule changes resulted in significantly enhanced performance 
 differentiation with the execution score being the main predictor of the final score. 
-Furthermore, in the article by \citet{ApparatusDifficulty2010}, the authors use regression, cluster, and ANOVA analysis to 
-analyze how difficulty scores predict overall score differently across different apparatuses. However, in this 
-article the authors found that while difficulty scores may have predictive tendencies for some apparatuses, 
+However, in the article by \citet{ApparatusDifficulty2010}, the authors found that while difficulty scores may 
+have predictive tendencies for some apparatuses, 
 the strength of the prediction varied drastically from apparatus to apparatus, with there being little to no 
-predictive ability for some apparatuses. Ultimately, the available literature on predicting 
-gymnastic success seems generally limited to how difficulty and execution scores predict overall score.
+predictive ability for some apparatuses.
 
@@
 gymnastics competitions and Olympic competition structure in order to identify the group of five athletes who will 
-enable the Team USA Olympic Women’s Artistic Gymnastics team to optimize success in Paris 2024.
+enable the Team USA Olympic Women’s Artistic Gymnastics team to optimize success.
 
@@
 
-To predict which of the United States athletes are most likely to medal on the various apparatuses, 
+For this paper, 
 I will be using the cleaned data that is provided by the UConn Sports Analytics Symposium data challenge 
-that includes data from major domestic and international gymnastic competitions from 2022 and 2023. 
-I have opted against using the older data from 2017 to 2021 as time, injuries, 
-and other factors can have a large impact on the success of a gymnast, so the greatest predictor
-of the Olympic outcomes in 2024 will be the most recent data.
+that includes data from major domestic and international gymnastic competitions from 2022 and 2023 only as time, injuries, 
+and other factors can have a large impact on the success of a gymnast.
 
@@
 
-For women, the data challenge presents the task of determining 
-which five athletes stand the greatest chance of winning the gold medal for the women's individual all-around,
-team all-around, Balance Beam, Floor Exercise, Uneven Bars, and Vault.
-
 In order to reduce the list of USA gymnasts to just five athletes, the proposed method in 
@@
 this alpha value should be reduced until the rank of the athletes coordinates with the order that seems visually most 
-logical based on the plots. While the parameters are to an extent subjective, in the final analysis the exact rank that 
+logical based on the plots.
+
+While the parameters are to an extent subjective, in the final analysis the exact rank that 
 is determined by the parameter is not terribly signifiant as the parameter values are used to determine the top five 
@@
 
-At various steps throughout the procedure large quantities of athletes were eliminated from consideration 
-based on various analytical decisions. For example, most athletes were eliminated from consideration as 
-only athletes that ranked in the top ten by mean score alone for each apparatus were inspected. This was a 
-reasonable elimination of data as the score values among the top ten candidates varied enough, often by over a 
-full point, to justify that athletes that never ranked in the top ten for a particular apparatus are not 
-competitive enough to medal at the Olympics. Furthermore, this list of athletes was also reduced by half by the 
-use of a subjectively determined parameter, but this decision is also justified as only two athletes from each 
-country can compete for an apparatus medal, so reducing the considered candidates to only the top five for each 
-apparatus is reasonable as it would be highly unlikely for the 6th best USA candidate for a particular apparatus 
-to medal at the Olympics.
-
 Notably, this algorithm is not powerful for strong athletes with few attempts on a particular apparatus as individuals 

### 2024-01-16 manuscript/submission.tex
proof reading for remaining errors

@@
 
-  With the whole world anticipating the success of the United States women's artistic gymnastics team, 
-  it is crucial that the team of five women that are selected to represent the United States 
-  are the athletes best suited to optimize success and maximize the expected medal count in Paris 2024. 
   This paper aims to answer the question of what metric should be used to judge the Olympic candidacy of USA 
@@
 
-For decades, gymnastics has been the most watched sport in the Summer Olympics and the United 
-States has been known for bringing gold medal-winning gymnasts to compete. In the 2020 
-Summer Olympics games in Tokyo, the United States women's artistic gymnastics team was the only team to take 
+In the 2020 Summer Olympic games in Tokyo, the United States women's artistic gymnastics team was the only team to take 
 home a medal in all six categories. Hence, the likelihood of the USA Olympic Women’s Artistic Gymnastics 
@@
 
-Currently there is no literature available relevant to predicting gymnastics outcomes at the 2024 
-Paris Summer Olympics or at recent olympics, but there is literature that relates to various aspects of 
+Currently there is no literature available relevant to predicting gymnastics outcomes at the Olympics, 
+but there is literature that relates to various aspects of 
 the data. For example, the article by \citet{ScienceOfGymnastics2021} aims to determine the 
@@
 
-As existing literature fails to suggest how data from major domestic and international gymnastics competitions 
-from the seasons leading up to the Summer Olympics can be used to identify the ``best'' Olympic team candidates, 
+As existing literature fails to suggest how data from major gymnastics competitions 
+can be used to identify the ``best'' Olympic team candidates, 
 the analytical method presented in this paper aims to outline a procedure that takes into account data from recent 
@@
      \item Using the plots, create a parameter for each apparatus that uses both mean score and standard 
-     deviation to identify which athletes are best suited to be considered to compete on behalf of the United 
-     States on each apparatus.
+     deviation to identify which athletes are best suited to be considered to compete on behalf of the USA on each apparatus.
      \begin{enumerate}
@@
 it is clear that Biles, Jones, and McClain are by far the best suited trio to compete for the team all-around medal. 
-Looking at plot of the combinations of four athletes, it is not clear whether Chiles, Carey, or 
+Looking at the plot of the combinations of four athletes, it is not clear whether Chiles, Carey, or 
 Blakely is best suited to be the fourth team all-around candidate as their means and standard deviations are very 
@@
 and Carey. Since Lincoln was not among our top candidates for an all-around medal, it would be logical to select her 
-as the fifth United States Olympic team member who does not compete in the all-around qualifying round. Additionally, 
+as the fifth USA team member who does not compete in the all-around qualifying round. Additionally, 
 since Carey is one of the candidates being considering for the all-around qualifying round and she is one of our superior 
-athletes on vault, it is reasonable to also select her to be the final member of the Olympic team.
+athletes on vault, it is reasonable to select her to be the final member of the Olympic team.
 
@@
 Using an analytical method dependent on mean and standard deviation derived parameters, this paper 
-outlines a procedure for identifying the Team USA Olympic Women’s Artistic Gymnastics team that will optimize 
+outlines a procedure for identifying the USA Olympic Women’s Artistic Gymnastics team that will optimize 
 success at the Olympics through numerically evaluating each USA athlete based on both their accuracy and precision. 
@@
 used as predictors at all.
-
-Ultimately, while this analytical method may not take into account all of the information and that that was available, 
-the method was able to identify a competitive group of athletes that represent the ``best'' athletes suited 
-to medal and optimize success in each of the Olympic events.
 
@@
 For men, the overall statistical method I used to determine the team of five male gymnasts that should be sent 
-to the 2024 Olympics was very similar, but varied when it came to determining the final fifth team member. After 
+to the 2024 Olympics was very similar, but varied when it came to determining the fifth team member. After 
 using the same method to determine the United States' best four male candidates for the team all-around qualification 
